### 2017-07-17 article_cvxpy.tex
whole working directory test

\documentclass[twocolumn,secnumarabic,amssymb, nobibnotes, aps, prl,superscriptaddress]{revtex4-1}
%\usepackage{acrofont}%NOTE: Comment out this line for the release version!
\newcommand{\revtex}{REV\TeX\ }
\newcommand{\classoption}[1]{\texttt{#1}}
\newcommand{\macro}[1]{\texttt{\textbackslash#1}}
\newcommand{\m}[1]{\macro{#1}}
\newcommand{\env}[1]{\texttt{#1}}
\setlength{\textheight}{9.5in}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[english]{babel}			
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{float}
\usepackage{datetime}				% custom date
\usepackage{dsfont}					% for indicator function 1
\usepackage{circuitikz}

\usepackage{url}					% clickable links
\usepackage{marvosym}				% symbols
\usepackage{wrapfig}				% wrapping text around figures
\usepackage[T1]{fontenc}			% font encoding
\usepackage{charter}

\usepackage{listings}				% for adding coloured code
\usepackage{color}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=none,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=mystyle}

	\newdateformat{mydate}{\monthname[\THEMONTH] \THEYEAR}

% Customize (header and) footerb
%\usepackage{fancyhdr}
%\pagestyle{fancy}
%\lfoot{	\footnotesize 
%		Mathematics Today magazine article \\
%		\Mundus\ \href{www.warwick.ac.uk/mathsys}{Mathematics for Real-World Systems CDT, University of Warwick and BT Research, Adastral Park}	\quad
		%\Telefon\ 555-5555											\quad
%\\		\Letter\ \href{mailto:R.Gowers@warwick.ac.uk}{Corresponding author: R.Gowers@warwick.ac.uk}
%	  }
%\cfoot{}
%\rfoot{\footnotesize ~\\ Page \thepage}
%\renewcommand{\headrulewidth}{0.0pt}	% no bar on top of page
%\renewcommand{\footrulewidth}{0.4pt}	% bar on bottom of page

%%% ---------------
%%% DEFINITIONS
%%% ---------------

\newcommand{\NewsItem}[1]{%
		\large #1 \vspace{4pt}
		\par \normalsize \normalfont}

\newcommand{\NewsAuthor}[1]{%
			\hfill \textsc{#1} \vspace{4pt}
			\par \normalfont}

%%% ---------------
%%% BEGIN DOCUMENT
%%% ---------------
\begin{document}
% Title	
% -----

\title{Convex optimisation in communications with cvxpy}

\author{Robert P.~Gowers}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Sami C.~Al-Izzi}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Timothy M.~Pollington}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Roger J.~W.~Hill}%
\affiliation{Department of Mathematics, University of Warwick}
\author{Keith Briggs}
\affiliation{BT, Adastral Park}

\maketitle
% -----

% Front article
% -----
	\NewsItem{``Nothing takes place in the world whose meaning is not that of some maximum or minimum.''}
	\NewsAuthor{Leonard Euler (1707-1783)}

\section{Introduction}
Convexity is an important property in optimisation. This is because if a problem is convex then the task of finding a global minimum is reduced to that of finding a local minimum. The importance of finding these minima efficiently in science and engineering has driven the development of software packages, such as \texttt{cvxpy}.

Here we show that many interesting problems in communications not only have a convex formulation (as shown in \cite{cvxpybook}), but can be easily implemented computationally using the \texttt{cvxpy} programming language. The ease of implementation of such problems makes \texttt{cvxpy} an invaluable tool for both students and researchers in many areas of science and engineering.
\subsection{Convex Sets and Functions}

If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}. More formally, for $x,y\in C$ and $\theta\in [0,1]$:
\begin{align}
\theta x + (1-\theta)y\in C.
\end{align}

In terms of a function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$. For $f$ to be \textit{convex} then the domain of $f$, $\textbf{dom} f$, must be a convex set and $\forall x,y\in \textbf{dom} f$ \cite[p.67]{cvxpybook}:
\begin{align}
f(\theta x + (1-\theta)y) \leq \theta f(x)+(1-\theta)f(y).
\end{align}
This means that the function is less than or equal to linear. This can be seen graphically in Fig~\ref{fig:convex}. A concave function can be made convex by the operation $f\to-f$.
\begin{figure}
\includegraphics[width=0.9\linewidth]{convex_function.pdf}
\caption{\label{fig:convex}A chord showing convexity of the function $x^4$.} 
\end{figure}

\subsection{Convex optimisation}
A \textit{convex optimisation problem} has three components:
\begin{itemize}
\item a convex \textit{objective function} $f_0(x)$,
\item $m$ convex \textit{inequality constraint functions} $f_i(x)$,
\item $k$ convex \textit{equality constraint functions} $g_j(x)$, 
\end{itemize}
where $f,g: \mathbb{R}^n \rightarrow \mathbb{R}$ \cite[p.141]{cvxpybook}. We seek an optimum $x^*\in \mathbb{R}^n$, where $f_0(x^*)$ is a minimum. Formally the problem is defined as:
\begin{align} \label{eq:cvxdefn}
&\text{minimise } && f_0(x) & \nonumber &\\
&\text{subject to } && f_i(x) \leq 0,\quad & i\in \{1,..,m\}\nonumber &\\
& && g_{j}(x)=0,\quad & j\in \{1,...,k\} &.
\end{align}

Any local optimum $x^*$ for a convex optimisation problem is also a global optimum \cite[pp.138-139]{cvxpybook}. An optimum of a convex optimisation problem may not be unique: consider the convex function $f(x) = \text{const}$, which has line of optima $x^*$.

\subsection{Disciplined convex programming}
\texttt{cvxpy} is a symbolic programming language for \textit{Python} developed by Diamond and Boyd at Stanford\cite{cvxpy}. It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex. If \texttt{cvxpy} finds that the function is convex, then interior point methods can be safely applied, which are guaranteed to find the optimal solution.

To implement DCP, the \texttt{cvxpy} package has a set of predefined functions in classes containing their curvature and sign. By only allowing certain operations with these known functions, general composition theorems from convex analysis can be applied to determine the convexity of the more complex expression. See Fig. \ref{fig:DCP}.

\begin{figure}
\includegraphics[width=0.7\linewidth]{DCP.pdf}
\caption{\label{fig:DCP}Application of DCP rules to a set of \texttt{cvxpy} functions, where $\text{entr}(x)=-x\log(x)$.  Figure adapted from the Stanford DCP Analyzer \cite{dcp}.}
\end{figure}

The set of available DCP functions do not define the complete set of convex functions. However, as we will show later, a large class of interesting convex problems can be written in DCP format.

We will show how \texttt{cvxpy} can be used simply to test a variety of optimisation problems, as a powerful easy-to-use tool for gaining insight into real-world problems.

\section{Real world applications}
\subsection{Water filling}
\begin{figure}
\includegraphics[width=1.0\linewidth]{water_filling_plot.pdf}
\caption{\label{fig:waterfilling}Water filling solution for three channels.}
\end{figure}

Convex optimisation can be used to solve the classic water filling problem.  In communications, this is where a total power $P$ must be assigned to $n$ different communication channels, with the objective of maximising the total communication rate.  The communication rate of the the $i$th channel, $r_i$, is given by \cite[p.245]{cvxpybook},

\begin{align}
r_i = \log(x_i+\alpha_i),
\end{align}
where $x_i$ is the power allocated to channel $i$ and $\alpha_i$ represents the floor above the baseline at which power can be added to the channel.  From Fig. \ref{fig:waterfilling}, we can see how this is analogous to filling an uneven basin to a constant level.

%Consider a bounded area of contiguous, equal-area patches $i$ of different elevations $\alpha_i$ (Fig.~\ref{fig:waterfilling}). The area is flooded to a certain level. Find the optimal height $x^{*}_i$ that uses a total amount of water of 1---this describes the famous `water filling' (or `water pouring') problem. It is also common to information theory, formulated by allocating power to communication channels, where each transmits at power $p_i$ and bandwidth $\alpha_i$, with channel rate $\log(\alpha_i+p_i)$\cite[p.245]{cvxpybook}.

The optimisation problem is then \cite{cvxpybook}:
\begin{align}
& \text{minimise} 
& & f_{0}(\textbf{x})=-\sum^{n}_{i=1}\log(\alpha_{i}+x_{i}),\quad\boldsymbol{\alpha} \succ \textbf{0}\nonumber\\
& \text{subject to} 
&& \textbf{x} \succeq \textbf{0} , \nonumber\\& && \sum^{n}_{i=1}x_{i}=\mathds{1}^{T}\textbf{x}=P
\end{align}
where symbols $\succ$, $\succeq$ denote elementwise inequalities between vectors or matrices.

This is a convex problem since $f_0(\textbf{x})$ has positive curvature within its domain, and the inequality and equality constraints are convex.

\subsubsection{Example \texttt{cvxpy} code in Python}
To indicate the brevity of code implementation in \texttt{cvxpy} we show an abridged version below:
\lstinputlisting[language=Python]{waterfilling.py}

\subsubsection{Computational complexity}
\texttt{cvxpy} employs different solvers for each problem and so they have different computational complexities; these were assessed by averaging the runtime over many runs.\\ 
In the case of water filling, for problem sizes up to 1000 channels, the computational time scaled linearly, Fig.~\ref{fig:waterfillingcomputcomplex}.Given that we have $n$ items in this problem and we apply the objective function to each channel independently, a computational complexity of $O(n)$ should be expected.

\begin{figure}
\includegraphics[width=0.9\linewidth]{water_filling_1000runs_1000buckets.pdf}
\caption{\label{fig:waterfillingcomputcomplex}Linear plot of computation time (wall time) of water filling against problem size, for 1000 runs.}
\end{figure}

\subsection{Maximising channel capacity}

Convex optimization can be used to find the channel capacity $C$ of a discrete memoryless channel. Consider a communication channel with input $X(t)\in\{1,2,...,n\}$ and output $Y(t)\in\{1,2,...m\}$. This means that the random variables $X$ and $Y$ can take $n$ and $m$ different values respectively.

In a discrete memoryless channel, the relation between the input and the output is given by the transition probability,
\begin{equation}
p_{ij} = \mathbb{P}(Y(t)=i|X(t)=j),
\end{equation} where these transition probabilities form the channel transition matrix $P$, with $P \in \mathbb{R}^{m\times n}$.  Assume that $X$ has a probability distribution denoted by $x\in\mathbb{R}^n$, meaning that,
\begin{equation}
x_j = \mathbb{P}(X(t) = j), \quad j=\{1,...,n\}.
\end{equation}
From Shannon \cite{shannon1949}, the channel capacity is given by the maximum possible mutual information, $I$, between $X$ and $Y$,
\begin{align}
C &= \sup_x I(X;Y), \quad \text{where},\\
I(X;Y) &= -\sum_{i=1}^{m}y_i\log_2 y_i+\sum_{j=1}^{n}\sum_{i=1}^{m}x_j p_{ij}\log_2 p_{ij}.
\end{align}

Given that $x\log x$ is convex for $x\geq 0$, we can formulate this as a convex optimisation problem,
\begin{align}
\text{minimise} \quad -I(X;Y), \\
\text{subject to} \quad \sum_{i=1}^{n}x_i = 1, \quad x \succeq 0.
\end{align} Here the constraints arise from $x$ describing a probability.

\subsubsection{Example \texttt{cvxpy} code}
Due to the built-in entropy function in \texttt{cvxpy}, \texttt{cvx.entr()}, the channel capacity problem is easy to write in DCP.

\lstinputlisting[language=Python]{channel_capacity.py}

\subsubsection{Computational complexity}
The computational complexity of the channel capacity problem follows a power law in \texttt{cvxpy}.  For $n$ up to 1000, the complexity is of order $\sim O(n^{2.5})$, Fig.~\ref{fig:channel_capacity_complexity}. Given that we are applying matrix multiplication to the power vector $\textbf{p}$, a complexity of at least $n^2$ would be expected.
\begin{figure}
\includegraphics[width=0.9\linewidth]{channel_capacity_complexity.pdf}
\caption{\label{fig:channel_capacity_complexity}Log-log plot of computation time (wall time) of channel capacity against problem size, for 1000 runs.}
\end{figure}

\subsection{Minimum power for a given SINR}
How can we minimise the total power consumption $P$ of $n$ transmitters each with power $p_i$, yet achieve a minimum SINR $\gamma_0$ for all $m$ receivers? This question is relevant to a telecoms company who want to offer a service at a minimum quality standard. We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and maximum power value that any transmitter can reach $P_{\text{max}}$:
		\begin{align*}
				&\underset{p}{\text{minimise}} \quad &&\sum_j p_j\\
				&\text{subject to} \quad &&p_j \leq P_{\max}\\
				& \quad &&p_j \geq 0\\
				& \quad &&\gamma_i \geq \gamma_0&&
		\end{align*}
The desired signal to receiver $i$ is denoted by $S_i = G_{ik}p_k$, while the interference to $i$ is $I_i = \sum_{j\neq k}G_{ij}p_j$. However DCP does not allow division of the optimisation variable $p_i$ so  
\begin{equation*}
  \gamma_i \geq \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i}\geq \gamma_0, \quad \forall i
\end{equation*}
was rearranged to:
\begin{equation*}
S_i-\gamma_0(\sigma_i + I_i)\geq 0, \quad \forall i
\end{equation*} which is DCP.
\subsubsection{Path gain}
The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$. Supposing that the desired signal to receiver $i$ is from transmitter $k$, the power received is,
\begin{equation}
p_{ik}^{\text{rec}} = G_{ik}p_k.
\end{equation}
The signal-to-interference-plus-noise ratio (SINR) is the strength of the desired signal $S_i$ relative to the interference power $I_i$ plus the background noise $\sigma_i$ at $i$. Denoting the SINR at $i$ by $\gamma_i$, we have
\begin{equation}
\gamma_i = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j}
=\frac{S_i}{\sigma_i+I_i}.
\end{equation}

In a physical context, the path gain from transmitter $j$ to receiver $i$ will depend on the distance, $d_{ij}$ between them.  Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is given by,

\begin{equation}
G_{ij} = k_i/d_{ij}^\alpha
\end{equation}

where $\alpha$ is the pathloss coefficient, $k$ is a proportionality constant specific to the receiver $i$.  For free space $\alpha = 2$, while for an urban environment $\alpha \sim 3.5$.  Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily implemented.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{scope}[every node/.style={circle,thick,draw}]
    \node (A) at (0,0) {i};
    \node (B) at (1,3) {j};
    \node (C) at (3,0) {k};
\end{scope}
\begin{scope}[
	every node/.style={fill=white,circle},
    every edge/.style={draw=black, thick}]
    \path [<->] (A) edge node {$d_{ik}$} (C);
    \path [<->] (B) edge node {$d_{ij}$} (A);
    %\path [<->] (C) edge node {$1$} (B);
\end{scope}
\end{tikzpicture}
\caption{Path lengths between receiver $i$ and transmitters $j$ and $k$.}\label{fig:spatial_diagram}
\end{figure}

\subsubsection{Example code}
The \texttt{cvxpy} implementation is shown below.
\lstinputlisting[language=Python]{minimisePgivenSINR.py}

\subsubsection{Computational Complexity}

\begin{figure}[H]
\includegraphics[width=0.9\linewidth]{magazineMinSINR.pdf}
\caption{\label{fig:MinSINR}Log-log plot of computation time (wall time) of minimum power problem against the problem size, for 25 runs.}
\end{figure}

The computational complexity of the power minimisation for $n$ up to 1000 is of order $\sim O(n^{2.8})$.

\section{Conclusions}
This article has shown that many well-known convex problems in communications can be written in a DCP format, meaning that they can be easily implemented in \texttt{cvxpy}.

Our example code demonstrates a key strength of \texttt{cvxpy}, which is that the translation from the mathematical description to python code is straightforward and clear.  Conversely, one can also infer the mathematical problem from reading the code.

The computational complexity of the problems examined had a clear trend which aligned with expectation.  This shows that convex optimisation solvers are robust to a variety of problem sizes and are scalable to at least problems of size 1000.

While all problems that can be written in DCP are convex, not all convex problems of interest can be written in DCP.  Over time, the library of available DCP functions in \texttt{cvxpy} has grown, increasing the scope of convex optimisation problems that \texttt{cvxpy} can solve.  This expansion of scope of \texttt{cvxpy} is ongoing, with version 1.0 under development and expected in the near future.

%\section{Further Work}
%While many problems are convex, others fall into a similar category of being \textit{quasi-convex}.  A quasi-convex function $f$ is one for which $\textbf{dom} f$ and every sublevel set of $f$ is convex.  An example of this is shown in Figure [?].  Quasi-convex problems cannot be solved directly using convex optimisation solvers, however the feasibility of a sublevel set can be checked.  This feasibility check can be used as a bisection method to find the solution.  A more thorough discussion of quasi-convex problems can be found in \cite{cvxpybook}chapter?.

%\section{Further applications}
\subsection*{Acknowledgements}
We would like to thank S. Johnson and S. Diamond for helpful discussions.

\section*{Appendix}
Full code can be found at\\ https://github.com/cvxgrp/cvxpy/tree/master\\/examples/communications.

\vspace{1cm}
%\section{Links \& references}
\bibliography{articleBib} 
\bibliographystyle{plain}

%\item DCP analyser http://dcp.stanford.edu/analyzer
% -----
\end{document}

### 2017-07-17 channel_capacity.py

@@ -1,0 +1,17 @@
+# n is the number of different input values
+# m is the number of different output values
+# x is probability distribution of the input signal X(t)
+x = cvx.Variable(rows=n,cols=1)
+# y is the probability distribution of the output signal Y(t)
+# P is the channel transition matrix
+y = P*x
+# I is the mutual information between x and y
+c = np.sum(P*np.log2(P),axis=0)
+I = c*x + cvx.sum_entries(cvx.entr(y))
+# Channel capacity maximised by maximising the mutual information
+obj = cvx.Minimize(-I)
+constraints = [cvx.sum_entries(x) == sum_x,x >= 0]
+# Form and solve problem
+prob = cvx.Problem(obj,constraints)
+prob.solve()
+

### 2017-07-17 minimisePgivenSINR.py

@@ -1,0 +1,22 @@
+# Declare variables
+I = np.zeros((n,m)) # interference power matrix
+S = np.zeros((n,m)) # signal power matrix
+delta = np.identity(n)
+S = G * delta # using gains matrix G
+I = G - S
+
+# Declare optimisation variable
+p = cvx.Variable(n)
+
+# Define objective function
+obj = cvx.Minimize(
+      cvx.sum_entries(p))
+
+# Declare constraints
+constraints =    [p >= 0,
+                  S*p-alpha*(I*p+sigma)>=0,
+                  p <= Pmax]
+
+# Solve problem
+prob = cvx.Problem(obj, constraints)
+prob.solve()

### 2017-07-17 waterfilling.py

@@ -1,0 +1,17 @@
+# Define variable (x) & parameter (a) with total power to allocate (sum_x) and number of channels (n).
+x = cvx.Variable(n)
+alpha = cvx.Parameter(n,sign='positive')
+alpha.value = a
+
+# Define objective function
+obj = cvx.Maximize(cvx.sum_entries
+                  (cvx.log(α + x))
+                  )
+
+# Define constraints
+constraints = [x >= 0,
+               cvx.sum_entries(x) - sum_x ==0]
+
+# Solve problem
+prob = cvx.Problem(obj, constraints)
+prob.solve()

### 2017-07-17 article_cvxpy.tex
waterfilling removed

@@
 \section{Real world applications}
-\subsection{Water filling}
-\begin{figure}
-\includegraphics[width=1.0\linewidth]{water_filling_plot.pdf}
-\caption{\label{fig:waterfilling}Water filling solution for three channels.}
-\end{figure}
-
-Convex optimisation can be used to solve the classic water filling problem.
-In communications, this is where a total power $P$ must be assigned to $n$ different communication channels, with the objective of maximising the total communication rate.
-The communication rate of the the $i$th channel, $r_i$, is given by \cite[p.245]{cvxpybook},
-
-\begin{align}
-r_i = \log(x_i+\alpha_i),
-\end{align}
-where $x_i$ is the power allocated to channel $i$ and $\alpha_i$ represents the floor above the baseline at which power can be added to the channel.
-From Fig.
-\ref{fig:waterfilling}, we can see how this is analogous to filling an uneven basin to a constant level.
-
-%Consider a bounded area of contiguous, equal-area patches $i$ of different elevations $\alpha_i$ (Fig.~\ref{fig:waterfilling}).
-The area is flooded to a certain level.
-Find the optimal height $x^{*}_i$ that uses a total amount of water of 1---this describes the famous `water filling' (or `water pouring') problem.
-It is also common to information theory, formulated by allocating power to communication channels, where each transmits at power $p_i$ and bandwidth $\alpha_i$, with channel rate $\log(\alpha_i+p_i)$\cite[p.245]{cvxpybook}.
-
-The optimisation problem is then \cite{cvxpybook}:
-\begin{align}
-& \text{minimise} 
-& & f_{0}(\textbf{x})=-\sum^{n}_{i=1}\log(\alpha_{i}+x_{i}),\quad\boldsymbol{\alpha} \succ \textbf{0}\nonumber\\
-& \text{subject to} 
-&& \textbf{x} \succeq \textbf{0} , \nonumber\\& && \sum^{n}_{i=1}x_{i}=\mathds{1}^{T}\textbf{x}=P
-\end{align}
-where symbols $\succ$, $\succeq$ denote elementwise inequalities between vectors or matrices.
-
-This is a convex problem since $f_0(\textbf{x})$ has positive curvature within its domain, and the inequality and equality constraints are convex.
-
-\subsubsection{Example \texttt{cvxpy} code in Python}
-To indicate the brevity of code implementation in \texttt{cvxpy} we show an abridged version below:
-\lstinputlisting[language=Python]{waterfilling.py}
-
-\subsubsection{Computational complexity}
-\texttt{cvxpy} employs different solvers for each problem and so they have different computational complexities; these were assessed by averaging the runtime over many runs.\\ 
-In the case of water filling, for problem sizes up to 1000 channels, the computational time scaled linearly, Fig.~\ref{fig:waterfillingcomputcomplex}.Given that we have $n$ items in this problem and we apply the objective function to each channel independently, a computational complexity of $O(n)$ should be expected.
-
-\begin{figure}
-\includegraphics[width=0.9\linewidth]{water_filling_1000runs_1000buckets.pdf}
-\caption{\label{fig:waterfillingcomputcomplex}Linear plot of computation time (wall time) of water filling against problem size, for 1000 runs.}
-\end{figure}
 
@@
 		\end{align*}
+(where symbols $\succ$, $\succeq$ denote elementwise inequalities between vectors or matrices.)
+
 The desired signal to receiver $i$ is denoted by $S_i = G_{ik}p_k$, while the interference to $i$ is $I_i = \sum_{j\neq k}G_{ij}p_j$.
@@
 \end{equation}
-
 In a physical context, the path gain from transmitter $j$ to receiver $i$ will depend on the distance, $d_{ij}$ between them.
@@
 \subsubsection{Example code}
-The \texttt{cvxpy} implementation is shown below.
-\lstinputlisting[language=Python]{minimisePgivenSINR.py}
+To indicate the brevity of code implementation in \texttt{cvxpy} we show an abridged version below: \lstinputlisting[language=Python]{minimisePgivenSINR.py}
 

### 2017-07-17 article_cvxpy.tex
cut down paper

@@
 
-\section{Real world applications}
-
-\subsection{Maximising channel capacity}
-
-Convex optimization can be used to find the channel capacity $C$ of a discrete memoryless channel.
-Consider a communication channel with input $X(t)\in\{1,2,...,n\}$ and output $Y(t)\in\{1,2,...m\}$.
-This means that the random variables $X$ and $Y$ can take $n$ and $m$ different values respectively.
-
-In a discrete memoryless channel, the relation between the input and the output is given by the transition probability,
-\begin{equation}
-p_{ij} = \mathbb{P}(Y(t)=i|X(t)=j),
-\end{equation} where these transition probabilities form the channel transition matrix $P$, with $P \in \mathbb{R}^{m\times n}$.
-Assume that $X$ has a probability distribution denoted by $x\in\mathbb{R}^n$, meaning that,
-\begin{equation}
-x_j = \mathbb{P}(X(t) = j), \quad j=\{1,...,n\}.
-\end{equation}
-From Shannon \cite{shannon1949}, the channel capacity is given by the maximum possible mutual information, $I$, between $X$ and $Y$,
-\begin{align}
-C &= \sup_x I(X;Y), \quad \text{where},\\
-I(X;Y) &= -\sum_{i=1}^{m}y_i\log_2 y_i+\sum_{j=1}^{n}\sum_{i=1}^{m}x_j p_{ij}\log_2 p_{ij}.
-\end{align}
-
-Given that $x\log x$ is convex for $x\geq 0$, we can formulate this as a convex optimisation problem,
-\begin{align}
-\text{minimise} \quad -I(X;Y), \\
-\text{subject to} \quad \sum_{i=1}^{n}x_i = 1, \quad x \succeq 0.
-\end{align} Here the constraints arise from $x$ describing a probability.
-
-\subsubsection{Example \texttt{cvxpy} code}
-Due to the built-in entropy function in \texttt{cvxpy}, \texttt{cvx.entr()}, the channel capacity problem is easy to write in DCP.
-
-\lstinputlisting[language=Python]{channel_capacity.py}
-
-\subsubsection{Computational complexity}
-The computational complexity of the channel capacity problem follows a power law in \texttt{cvxpy}.
-For $n$ up to 1000, the complexity is of order $\sim O(n^{2.5})$, Fig.~\ref{fig:channel_capacity_complexity}.
-Given that we are applying matrix multiplication to the power vector $\textbf{p}$, a complexity of at least $n^2$ would be expected.
-\begin{figure}
-\includegraphics[width=0.9\linewidth]{channel_capacity_complexity.pdf}
-\caption{\label{fig:channel_capacity_complexity}Log-log plot of computation time (wall time) of channel capacity against problem size, for 1000 runs.}
-\end{figure}
-
-\subsection{Minimum power for a given SINR}
+\section{Minimum power for a given SINR}
 How can we minimise the total power consumption $P$ of $n$ transmitters each with power $p_i$, yet achieve a minimum SINR $\gamma_0$ for all $m$ receivers?
@@
 \end{equation*} which is DCP.
-\subsubsection{Path gain}
+\subsection{Path gain}
 The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$.
@@
 
-\subsubsection{Example code}
+\subsection{Example code}
 To indicate the brevity of code implementation in \texttt{cvxpy} we show an abridged version below: \lstinputlisting[language=Python]{minimisePgivenSINR.py}
 
-\subsubsection{Computational Complexity}
-
-\begin{figure}[H]
-\includegraphics[width=0.9\linewidth]{magazineMinSINR.pdf}
-\caption{\label{fig:MinSINR}Log-log plot of computation time (wall time) of minimum power problem against the problem size, for 25 runs.}
-\end{figure}
-
-The computational complexity of the power minimisation for $n$ up to 1000 is of order $\sim O(n^{2.8})$.
-
 \section{Conclusions}
-This article has shown that many well-known convex problems in communications can be written in a DCP format, meaning that they can be easily implemented in \texttt{cvxpy}.
+This article has shown that a well-known convex problem in communications can be written in a DCP format, meaning that they can be easily implemented in \texttt{cvxpy}.
 
@@
 Conversely, one can also infer the mathematical problem from reading the code.
-
-The computational complexity of the problems examined had a clear trend which aligned with expectation.
-This shows that convex optimisation solvers are robust to a variety of problem sizes and are scalable to at least problems of size 1000.
 

### 2017-07-17 article_cvxpy.tex
test
introduction made better

@@
 
-Here we show that many interesting problems in communications not only have a convex formulation (as shown in \cite{cvxpybook}), but can be easily implemented computationally using the \texttt{cvxpy} programming language.
-The ease of implementation of such problems makes \texttt{cvxpy} an invaluable tool for both students and researchers in many areas of science and engineering.
+Here we show that an interesting problem in communications not only has a convex formulation (as shown in \cite{cvxpybook}), but can be easily implemented computationally using the \texttt{cvxpy} Python module.
+The ease of implementation makes \texttt{cvxpy} an invaluable tool for both students and researchers in many areas of science and engineering.
 \subsection{Convex Sets and Functions}

### 2017-07-17 article_cvxpy.tex
changes made

@@
 The ease of implementation makes \texttt{cvxpy} an invaluable tool for both students and researchers in many areas of science and engineering.
-\subsection{Convex Sets and Functions}
+\subsection{Convex Functions}
 
-If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}. More formally, for $x,y\in C$ and $\theta\in [0,1]$:
-\begin{align}
-\theta x + (1-\theta)y\in C.
-\end{align}
+%If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}. More formally, for $x,y\in C$ and $\theta\in [0,1]$:
+%\begin{align}
+%\theta x + (1-\theta)y\in C.
+%\end{align}
 
-In terms of a function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$.
-For $f$ to be \textit{convex} then the domain of $f$, $\textbf{dom} f$, must be a convex set and $\forall x,y\in \textbf{dom} f$ \cite[p.67]{cvxpybook}:
+A function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$, is \textit{convex} if $\forall x,y\in \textbf{dom} f$ and $0 \leq \theta \leq 1$ \cite[p.67]{cvxpybook}:
 \begin{align}
@@
 \end{align}
-This means that the function is less than or equal to linear. This can be seen graphically in Fig~\ref{fig:convex}. A concave function can be made convex by the operation $f\to-f$.
+This means that the function is less than or equal to linear, as shown in Fig~\ref{fig:convex}. %A concave function can be made convex by the operation $f\to-f$.
 \begin{figure}
@@
 \end{itemize}
-where $f,g: \mathbb{R}^n \rightarrow \mathbb{R}$ \cite[p.141]{cvxpybook}. We seek an optimum $x^*\in \mathbb{R}^n$, where $f_0(x^*)$ is a minimum. Formally the problem is defined as:
+where $f,g: \mathbb{R}^n \rightarrow \mathbb{R}$ \cite[p.141]{cvxpybook}. We seek an optimum, $x^*\in \mathbb{R}^n$, where $f_0(x^*)$ is a minimum. Formally the problem is defined as:
 \begin{align} \label{eq:cvxdefn}
@@
 
-Any local optimum $x^*$ for a convex optimisation problem is also a global optimum \cite[pp.138-139]{cvxpybook}.
-An optimum of a convex optimisation problem may not be unique: consider the convex function $f(x) = \text{const}$, which has line of optima $x^*$.
+Any local optimum $x^*$ for a convex optimisation problem is also a global optimum \cite[pp.138-139]{cvxpybook}, however an optimum may not be unique.
 
 \subsection{Disciplined convex programming}
-\texttt{cvxpy} is a symbolic programming language for \textit{Python} developed by Diamond and Boyd at Stanford\cite{cvxpy}.
+\texttt{cvxpy} is a symbolic programming module for \textit{Python} developed at Stanford\cite{cvxpy}.
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
-If \texttt{cvxpy} finds that the function is convex, then interior point methods can be safely applied, which are guaranteed to find the optimal solution.
-
-To implement DCP, the \texttt{cvxpy} package has a set of predefined functions in classes containing their curvature and sign.
+To implement DCP, \texttt{cvxpy} has a set of predefined functions in classes containing their curvature and sign.
 By only allowing certain operations with these known functions, general composition theorems from convex analysis can be applied to determine the convexity of the more complex expression.
@@
 \ref{fig:DCP}.
+If this is the case, then interior point methods guarantee an optimal solution.
 

### 2017-07-17 article_cvxpy.tex
improvements made

@@
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
-To implement DCP, \texttt{cvxpy} has a set of predefined functions in classes containing their curvature and sign.
-By only allowing certain operations with these known functions, general composition theorems from convex analysis can be applied to determine the convexity of the more complex expression.
+This is implemented using predefined classes containing functions with their curvature and sign, and using general composition theorems from convex analysis.
 See Fig.
@@
 
-The set of available DCP functions do not define the complete set of convex functions. However, as we will show later, a large class of interesting convex problems can be written in DCP format.
-
-We will show how \texttt{cvxpy} can be used simply to test a variety of optimisation problems, as a powerful easy-to-use tool for gaining insight into real-world problems.
-
-\section{Minimum power for a given SINR}
+\section{Example: power minimisation in communications}
 How can we minimise the total power consumption $P$ of $n$ transmitters each with power $p_i$, yet achieve a minimum SINR $\gamma_0$ for all $m$ receivers?

### 2017-07-17 article_cvxpy.tex
Shortened version for review

@@
 This means that the function is less than or equal to linear, as shown in Fig~\ref{fig:convex}. %A concave function can be made convex by the operation $f\to-f$.
-\begin{figure}
+\begin{figure}[h!]
 \includegraphics[width=0.9\linewidth]{convex_function.pdf}
@@
 This is implemented using predefined classes containing functions with their curvature and sign, and using general composition theorems from convex analysis.
-See Fig.
-\ref{fig:DCP}.
 If this is the case, then interior point methods guarantee an optimal solution.
 
-\begin{figure}
-\includegraphics[width=0.7\linewidth]{DCP.pdf}
-\caption{\label{fig:DCP}Application of DCP rules to a set of \texttt{cvxpy} functions, where $\text{entr}(x)=-x\log(x)$.  Figure adapted from the Stanford DCP Analyzer \cite{dcp}.}
-\end{figure}
-
 \section{Example: power minimisation in communications}
-How can we minimise the total power consumption $P$ of $n$ transmitters each with power $p_i$, yet achieve a minimum SINR $\gamma_0$ for all $m$ receivers?
+For a real world example consider a system of $n$ transmitters and $m$ receivers distributed in $2D$ Euclidian space.
+Each of the transmitters has power $p_i$.
+How can we minimise the total power consumption $P$ of transmitters, yet achieve a minimum Signal to Interference plus Noise Ratio (SINR), $\gamma_0$, for all receivers?
 This question is relevant to a telecoms company who want to offer a service at a minimum quality standard.
@@
 \end{align*}
-(where symbols $\succ$, $\succeq$ denote elementwise inequalities between vectors or matrices.)
+where symbols $\succ$, $\succeq$ denote element-wise inequalities between vectors or matrices.
 
@@
 S_i-\gamma_0(\sigma_i + I_i)\geq 0, \quad \forall i
-\end{equation*} which is DCP.
+\end{equation*} which is affine, and hence DCP.
+
 \subsection{Path gain}
@@
 where $\alpha$ is the pathloss coefficient, $k$ is a proportionality constant specific to the receiver $i$.
-For free space $\alpha = 2$, while for an urban environment $\alpha \sim 3.5$.
+For free space $\alpha = 2$, while for an urban environment $\alpha \sim 3.5$ \textbf{CITE THIS}.
 Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily implemented.
@@
 
-\section{Conclusions}
-This article has shown that a well-known convex problem in communications can be written in a DCP format, meaning that they can be easily implemented in \texttt{cvxpy}.
+\section{Outlook}
+The authors hope that this article shows the ease with the which \texttt{cvxpy} can be brought to bare on simple ``toy'' problems of real world relevance.
+We also believe that this is an invaluable resource for researchers wanting test the applicability of convex optimization in new fields.
 
-Our example code demonstrates a key strength of \texttt{cvxpy}, which is that the translation from the mathematical description to python code is straightforward and clear.
-Conversely, one can also infer the mathematical problem from reading the code.
+The module could also be easily incorporated into a course on optimization, providing students with a simple environment with which to implement techniques for convex optimization.
 
-While all problems that can be written in DCP are convex, not all convex problems of interest can be written in DCP.
+%While all problems that can be written in DCP are convex, not all convex problems of interest can be written in DCP.
 Over time, the library of available DCP functions in \texttt{cvxpy} has grown, increasing the scope of convex optimisation problems that \texttt{cvxpy} can solve.

### 2017-07-17 article_cvxpy.tex
Shortened version for review

@@
 \section{Example: power minimisation in communications}
-For a real world example consider a system of $n$ transmitters and $m$ receivers distributed in $2D$ Euclidian space.
+For a real world example consider a system of $n$ transmitters and $m$ receivers distributed in $2$D Euclidian space.
 Each of the transmitters has power $p_i$.

### 2017-07-17 article_cvxpy.tex
Shortened version for review

@@
 \subsection{Disciplined convex programming}
-\texttt{cvxpy} is a symbolic programming module for \textit{Python} developed at Stanford\cite{cvxpy}.
+\texttt{cvxpy} is a symbolic programming module for \textit{Python} developed at Stanford \cite{cvxpy}.
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
-This is implemented using predefined classes containing functions with their curvature and sign, and using general composition theorems from convex analysis.
+This is implemented using predefined classes containing functions with their curvature and sign, and using general composition theorems from convex analysis \cite{dcp}.
 If this is the case, then interior point methods guarantee an optimal solution.
@@
 \section{Example: power minimisation in communications}
-For a real world example consider a system of $n$ transmitters and $m$ receivers distributed in $2$D Euclidian space.
-Each of the transmitters has power $p_i$.
+For a real world example consider a system of $n$ transmitters and $m$ receivers distributed in $2$D Euclidian space where each of the transmitters has power $p_i$ \cite{shannon1949}.
 How can we minimise the total power consumption $P$ of transmitters, yet achieve a minimum Signal to Interference plus Noise Ratio (SINR), $\gamma_0$, for all receivers?
@@
 where $\alpha$ is the pathloss coefficient, $k$ is a proportionality constant specific to the receiver $i$.
-For free space $\alpha = 2$, while for an urban environment $\alpha \sim 3.5$ \textbf{CITE THIS}.
+For free space $\alpha = 2$, while for an urban environment $\alpha \sim 3.5$ \cite{hata1980}.
 Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily implemented.
@@
 The authors hope that this article shows the ease with the which \texttt{cvxpy} can be brought to bare on simple ``toy'' problems of real world relevance.
-We also believe that this is an invaluable resource for researchers wanting test the applicability of convex optimization in new fields.
+We believe that this is an invaluable resource for researchers wanting test the applicability of convex optimization in new fields.
 

### 2017-07-18 article_cvxpy.tex
Tim edits to incorporate KBs comments, remove curly ineqs and double SINR expl

@@
 \usepackage{circuitikz}		
-
 \usepackage{url}					% clickable links
@@
 \usepackage{charter} 		
-
 \usepackage{listings}				% for adding coloured code
@@
 
-\title{Convex optimisation in communications with cvxpy}
-
+\title{Convex optimisation in communications with \texttt{cvxpy}}
 \author{Robert P.~Gowers}%
@@
 
-Here we show that an interesting problem in communications not only has a convex formulation (as shown in \cite{cvxpybook}), but can be easily implemented computationally using the \texttt{cvxpy} Python module.
-The ease of implementation makes \texttt{cvxpy} an invaluable tool for both students and researchers in many areas of science and engineering.
-\subsection{Convex Functions}
+Here we show that an interesting problem in communications has a convex formulation that can be easily implemented computationally using the \texttt{cvxpy} \textit{Python} module.
+This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering.
 
+\subsection{Convex functions}
 %If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}. More formally, for $x,y\in C$ and $\theta\in [0,1]$:
@@
 \end{align}
-This means that the function is less than or equal to linear, as shown in Fig~\ref{fig:convex}. %A concave function can be made convex by the operation $f\to-f$.
+This means that the function is less than or equal to linear, as shown in Fig.~\ref{fig:convex}. %A concave function can be made convex by the operation $f\to-f$.
 \begin{figure}[h!]
@@
 \subsection{Disciplined convex programming}
-\texttt{cvxpy} is a symbolic programming module for \textit{Python} developed at Stanford \cite{cvxpy}.
+\texttt{cvxpy} is a symbolic programming module for \textit{Python}\cite{cvxpy}.
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
 This is implemented using predefined classes containing functions with their curvature and sign, and using general composition theorems from convex analysis \cite{dcp}.
-If this is the case, then interior point methods guarantee an optimal solution.
+If DCP rules can be applied then interior point methods guarantee an optimal solution.
 
 \section{Example: power minimisation in communications}
-For a real world example consider a system of $n$ transmitters and $m$ receivers distributed in $2$D Euclidian space where each of the transmitters has power $p_i$ \cite{shannon1949}.
+For a real-world example consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
+The signal-to-interference-plus-noise ratio (SINR) is the strength of the desired signal $S$ relative to the interference power $I$ plus the background noise $\sigma$ at a receiver.
 How can we minimise the total power consumption $P$ of transmitters, yet achieve a minimum Signal to Interference plus Noise Ratio (SINR), $\gamma_0$, for all receivers?
 This question is relevant to a telecoms company who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and maximum power value that any transmitter can reach $P_{\text{max}}$:
+We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and a maximum power constraint $P_{\text{max}}$ of any transmitter:
 \begin{align*}
@@
 & \quad &&p_j \geq 0\\
-& \quad &&\gamma_i \geq \gamma_0&&
+& \quad &&\gamma_i \geq \gamma_0.&&
 \end{align*}
-where symbols $\succ$, $\succeq$ denote element-wise inequalities between vectors or matrices.
 
-The desired signal to receiver $i$ is denoted by $S_i = G_{ik}p_k$, while the interference to $i$ is $I_i = \sum_{j\neq k}G_{ij}p_j$.
-However DCP does not allow division of the optimisation variable $p_i$ so
+The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, while the interference at $i$ is $I_i = \sum_{j\neq k}G_{ij}p_j$. However DCP does not allow division of the optimisation variable $p_i$ so  
 \begin{equation*}
@@
 S_i-\gamma_0(\sigma_i + I_i)\geq 0, \quad \forall i
-\end{equation*} which is affine, and hence DCP.
+\end{equation*} which is affine, and hence a DCP function.
 
@@
 \end{equation}
-The signal-to-interference-plus-noise ratio (SINR) is the strength of the desired signal $S_i$ relative to the interference power $I_i$ plus the background noise $\sigma_i$ at $i$.
 Denoting the SINR at $i$ by $\gamma_i$, we have
@@
 \end{equation}
-In a physical context, the path gain from transmitter $j$ to receiver $i$ will depend on the distance, $d_{ij}$ between them.
-Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is given by,
-
+In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$ between them.
+Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is:
 \begin{equation}
@@
 \end{equation}
-
-where $\alpha$ is the pathloss coefficient, $k$ is a proportionality constant specific to the receiver $i$.
-For free space $\alpha = 2$, while for an urban environment $\alpha \sim 3.5$ \cite{hata1980}.
-Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily implemented.
+where $\alpha$ is the pathloss coefficient and $k$ is a proportionality constant specific to the receiver $i$.
+For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}.
+Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily incorporated.
 
@@
 \end{tikzpicture}
-\caption{Path lengths between receiver $i$ and transmitters $j$ and $k$.}\label{fig:spatial_diagram}
+\caption{\label{fig:pathgain}Path lengths between receiver $i$ and transmitters $j$ and $k$.}
 \end{figure}
@@
 \subsection{Example code}
-To indicate the brevity of code implementation in \texttt{cvxpy} we show an abridged version below: \lstinputlisting[language=Python]{minimisePgivenSINR.py}
+To indicate the brevity of code implementation in \texttt{cvxpy} we show an abridged version below: \lstinputlisting[language=Python,mathescape=true]{minimisePgivenSINR.py}
 
 \section{Outlook}
-The authors hope that this article shows the ease with the which \texttt{cvxpy} can be brought to bare on simple ``toy'' problems of real world relevance.
-We believe that this is an invaluable resource for researchers wanting test the applicability of convex optimization in new fields.
+The authors hope that this article shows the utility of \texttt{cvxpy} for simple ``toy'' problems of real-world relevance.
+We believe it is an invaluable resource for researchers wanting test the applicability of convex optimisation in new fields.
 
-The module could also be easily incorporated into a course on optimization, providing students with a simple environment with which to implement techniques for convex optimization.
+The module could also be easily incorporated into a course on optimisation, providing students with an accessible environment to practise techniques for convex optimisation.
 
@@
 %\section{Further applications}
-\subsection*{Acknowledgements}
-We would like to thank S. Johnson and S. Diamond for helpful discussions.
+\subsection*{Acknowledgements and appendix}
+We would like to thank S.
+Johnson and S.
+Diamond for helpful discussions.
+Full code for other communication examples can be found at\\ https://github.com/cvxgrp/cvxpy/tree/master\\/examples/communications.
 
-\section*{Appendix}
-Full code can be found at\\ https://github.com/cvxgrp/cvxpy/tree/master\\/examples/communications.
-
-\vspace{1cm}
+\vspace{0.2cm}
 %\section{Links \& references}

### 2017-07-18 minimisePgivenSINR.py

@@ -1,21 +1,19 @@
-# Declare variables
-I = np.zeros((n,m)) # interference power matrix
-S = np.zeros((n,m)) # signal power matrix
+# Define variables
 delta = np.identity(n)
-S = G * delta # using gains matrix G
+S = G * delta
 I = G - S
 
-# Declare optimisation variable
+# Define optimisation variable
 p = cvx.Variable(n)
 
 # Define objective function
 obj = cvx.Minimize(
       cvx.sum_entries(p))
 
-# Declare constraints
-constraints =    [p >= 0,
-                  S*p-alpha*(I*p+sigma)>=0,
-                  p <= Pmax]
+# Define constraints
+constraints = [p >= 0,
+               S * p - $\alpha$ * (I * p + $\sigma$) >= 0,
+               p <= Pmax]
 
 # Solve problem
 prob = cvx.Problem(obj, constraints)

### 2017-07-18 article_cvxpy.tex
minor chnages

@@
 How can we minimise the total power consumption $P$ of transmitters, yet achieve a minimum Signal to Interference plus Noise Ratio (SINR), $\gamma_0$, for all receivers?
-This question is relevant to a telecoms company who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and a maximum power constraint $P_{\text{max}}$ of any transmitter:
+This question is relevant to telecoms companies who want to offer a service at a minimum quality standard.
+We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and a maximum power constraint $P_{\text{max}}$ of each transmitter:
 \begin{align*}
@@
 \end{equation*}
-was rearranged to:
+was rearranged to,
 \begin{equation*}
@@
 \subsection{Example code}
-To indicate the brevity of code implementation in \texttt{cvxpy} we show an abridged version below: \lstinputlisting[language=Python,mathescape=true]{minimisePgivenSINR.py}
+To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below: \lstinputlisting[language=Python,mathescape=true]{minimisePgivenSINR.py}
 

### 2017-07-18 article_cvxpy.tex
Tim edits following meet with Rob

--- 2017-07-18 article_cvxpy.tex
@@
 \author{Robert P.~Gowers}%
-\affiliation{Department of Mathematics, University of Warwick}
 \author{Sami C.~Al-Izzi}%
-\affiliation{Department of Mathematics, University of Warwick}
 \author{Timothy M.~Pollington}%
-\affiliation{Department of Mathematics, University of Warwick}
 \author{Roger J.~W.~Hill}%
@@
 \affiliation{BT, Adastral Park}
+\maketitle
 
-\maketitle
 % -----
@@
 This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering.
+First let us introduce some basic convexity concepts.
 
@@
 \section{Outlook}
-The authors hope that this article shows the utility of \texttt{cvxpy} for simple ``toy'' problems of real-world relevance.
+The authors hope that this article shows the utility of \texttt{cvxpy} for simple `toy' problems of real-world relevance.
 We believe it is an invaluable resource for researchers wanting test the applicability of convex optimisation in new fields.
@@
 The module could also be easily incorporated into a course on optimisation, providing students with an accessible environment to practise techniques for convex optimisation.
+Full code for other communication examples can be found at https://github.com/cvxgrp/cvxpy/\\tree/master/examples/communications.
 
@@
 %\section{Further applications}
-\subsection*{Acknowledgements and appendix}
-We would like to thank S.
-Johnson and S.
-Diamond for helpful discussions.
-Full code for other communication examples can be found at\\ https://github.com/cvxgrp/cvxpy/tree/master\\/examples/communications.
+\subsection*{Acknowledgements}
+We would like to thank S.~Johnson from MathSys and S.~Diamond for helpful discussions.
 

### 2017-08-08 article_cvxpy.tex
Rob changes 08/08/17

@@
 \usepackage{color}
+%\setlength{\parindent}{0pt} % to not indent any paragraphs
 \definecolor{codegreen}{rgb}{0,0.6,0}
@@
 
-% Customize (header and) footerb
-%\usepackage{fancyhdr}
-%\pagestyle{fancy}
-%\lfoot{	\footnotesize 
-%		Mathematics Today magazine article \\
-%		\Mundus\ \href{www.warwick.ac.uk/mathsys}{Mathematics for Real-World Systems CDT, University of Warwick and BT Research, Adastral Park}	\quad
-		%\Telefon\ 555-5555											\quad
-%\\		\Letter\ \href{mailto:R.Gowers@warwick.ac.uk}{Corresponding author: R.Gowers@warwick.ac.uk}
-%	  }
-%\cfoot{}
-%\rfoot{\footnotesize ~\\ Page \thepage}
-%\renewcommand{\headrulewidth}{0.0pt}	% no bar on top of page
-%\renewcommand{\footrulewidth}{0.4pt}	% bar on bottom of page
-
 %%% ---------------
@@
 
-%%% ---------------
-%%% BEGIN DOCUMENT
-%%% ---------------
 \begin{document}
@@
 % -----
-	\NewsItem{``Nothing takes place in the world whose meaning is not that of some maximum or minimum.''}
+	\NewsItem{\noindent``Nothing takes place in the world whose meaning is not that of some maximum or minimum.''}
 	\NewsAuthor{Leonard Euler (1707-1783)}
@@
 \section{Introduction}
-Convexity is an important property in optimisation.
+\noindent Convexity is an important property in optimisation.
 This is because if a problem is convex then the task of finding a global minimum is reduced to that of finding a local minimum.
@@
 
-A function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$, is \textit{convex} if $\forall x,y\in \textbf{dom} f$ and $0 \leq \theta \leq 1$ \cite[p.67]{cvxpybook}:
+\noindent A function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$, is \textit{convex} if $\forall x,y\in \textbf{dom} f$ and $0 \leq \theta \leq 1$ \cite[p.67]{cvxpybook}:
 \begin{align}
@@
 \subsection{Convex optimisation}
-A \textit{convex optimisation problem} has three components:
+\noindent A \textit{convex optimisation problem} has three components:
 \begin{itemize}
@@
 \subsection{Disciplined convex programming}
-\texttt{cvxpy} is a symbolic programming module for \textit{Python}\cite{cvxpy}.
+\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for \textit{Python}\cite{cvxpy}.
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
@@
 \section{Example: power minimisation in communications}
-For a real-world example consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
+\noindent For a real-world example consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
 The signal-to-interference-plus-noise ratio (SINR) is the strength of the desired signal $S$ relative to the interference power $I$ plus the background noise $\sigma$ at a receiver.
@@
 \subsection{Path gain}
-The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$.
+\noindent The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$.
 Supposing that the desired signal to receiver $i$ is from transmitter $k$, the power received is,
@@
 \subsection{Example code}
-To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below: \lstinputlisting[language=Python,mathescape=true]{minimisePgivenSINR.py}
+\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below: \lstinputlisting[language=Python,mathescape=true]{minimisePgivenSINR.py}
 
 \section{Outlook}
-The authors hope that this article shows the utility of \texttt{cvxpy} for simple `toy' problems of real-world relevance.
+\noindent The authors hope that this article shows the utility of \texttt{cvxpy} for simple `toy' problems of real-world relevance.
 We believe it is an invaluable resource for researchers wanting test the applicability of convex optimisation in new fields.

### 2017-08-08 minimisePgivenSINR.py

@@ -1,7 +1,22 @@
+import cvxpy as cvx
+import numpy as np
+
+n = 3
+k = 1
+d = np.random.rand(n,n)
+d_s = 0.5*(d+d.T)
+
+G = np.zeros((n,n))
+G = k/d_s**3.5
+
 # Define variables
-delta = np.identity(n)
-S = G * delta
+$\delta$ = np.identity(n)
+S = G * $\delta$
 I = G - S
+
+sigma = 0.1*np.ones(n)
+gamma = 1
+Pmax = 1
 
 # Define optimisation variable
 p = cvx.Variable(n)
@@ -12,9 +27,12 @@ obj = cvx.Minimize(
 
 # Define constraints
 constraints = [p >= 0,
-               S * p - $\alpha$ * (I * p + $\sigma$) >= 0,
+               S * p - $\gamma$ * (I * p + $\sigma$) >= 0,
                p <= Pmax]
 
-# Solve problem
+# Solve problem and print solution
 prob = cvx.Problem(obj, constraints)
 prob.solve()
+print("Solution status = %s"%(prob.status))
+print("Optimal solution = %s"%(prob.value))
+print("Power settings = %s"%(p.value))

### 2017-08-08 article_cvxpy.tex
Rob changes, slight tweaks

@@
 \section{Example: power minimisation in communications}
-\noindent For a real-world example consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
-The signal-to-interference-plus-noise ratio (SINR) is the strength of the desired signal $S$ relative to the interference power $I$ plus the background noise $\sigma$ at a receiver.
-How can we minimise the total power consumption $P$ of transmitters, yet achieve a minimum Signal to Interference plus Noise Ratio (SINR), $\gamma_0$, for all receivers?
+\noindent To demonstrate the applicability \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
+In this problem we are constrained to having a minimum signal-to-interference-plus-noise ratio (SINR) at each receiver; the strength of the desired signal, $S$, relative to the interference power, $I$, plus the background noise, $\sigma$, at a receiver.
+How can we minimise the total power consumption, $P$, of transmitters, yet achieve this minimum SINR, $\gamma_0$, for all receivers?
 This question is relevant to telecoms companies who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and a maximum power constraint $P_{\text{max}}$ of each transmitter:
+We formulate the problem with a given square path gain matrix, $G$, background noise level $\sigma$ and a maximum power constraint $P_{\text{max}}$ of each transmitter:
 \begin{align*}

### 2017-08-08 minimisePgivenSINR.py

@@ -1,22 +1,22 @@
 import cvxpy as cvx
 import numpy as np
 
+# Define variables
 n = 3
-k = 1
+k = 1.0
 d = np.random.rand(n,n)
 d_s = 0.5*(d+d.T)
 
 G = np.zeros((n,n))
 G = k/d_s**3.5
 
-# Define variables
 $\delta$ = np.identity(n)
 S = G * $\delta$
 I = G - S
 
 sigma = 0.1*np.ones(n)
-gamma = 1
-Pmax = 1
+gamma = 1.0
+Pmax = 1.0
 
 # Define optimisation variable
 p = cvx.Variable(n)

### 2017-08-13 minimisePgivenSINR.py
Tim tweak to py file
Extra greek letters and white spaces around arith. operators for syntax consistency.

@@ -5,17 +5,17 @@ import numpy as np
 n = 3
 k = 1.0
 d = np.random.rand(n,n)
-d_s = 0.5*(d+d.T)
+d_s = 0.5 * (d + d.T)
 
 G = np.zeros((n,n))
-G = k/d_s**3.5
+G = k / d_s ** 3.5
 
 $\delta$ = np.identity(n)
 S = G * $\delta$
 I = G - S
 
-sigma = 0.1*np.ones(n)
-gamma = 1.0
+$\sigma$ = 0.1 * np.ones(n)
+$\gamma$ = 1.0
 Pmax = 1.0
 
 # Define optimisation variable

### 2017-08-13 article_cvxpy.tex
Tim tweak to tex file, note PDF uncompiled

@@
 \section{Example: power minimisation in communications}
-\noindent To demonstrate the applicability \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
+\noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
 In this problem we are constrained to having a minimum signal-to-interference-plus-noise ratio (SINR) at each receiver; the strength of the desired signal, $S$, relative to the interference power, $I$, plus the background noise, $\sigma$, at a receiver.
@@
 \noindent The authors hope that this article shows the utility of \texttt{cvxpy} for simple `toy' problems of real-world relevance.
-We believe it is an invaluable resource for researchers wanting test the applicability of convex optimisation in new fields.
+We believe it is an invaluable resource for researchers wanting to test the applicability of convex optimisation in new fields.
 

### 2017-10-13 article_cvxpy.tex
added email addresses, moved plots a bit

@@
 \author{Robert P.~Gowers}%
+\email{r.gowers@warwick.ac.uk}
 \author{Sami C.~Al-Izzi}%
+\email{s.al-izzi@warwick.ac.uk}
 \author{Timothy M.~Pollington}%
+\email{t.pollington@warwick.ac.uk}
 \author{Roger J.~W.~Hill}%
+\email{r.hill.3@warwick.ac.uk}
 \affiliation{Department of Mathematics, University of Warwick}
 \author{Keith Briggs}
+\email{keith.briggs@bt.com}
 \affiliation{BT, Adastral Park}
+%\affiliation{r.gowers@warwick.ac.uk}
 \maketitle
@@
 This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering.
-First let us introduce some basic convexity concepts.
+First let us introduce what convexity means.
 
@@
 This means that the function is less than or equal to linear, as shown in Fig.~\ref{fig:convex}. %A concave function can be made convex by the operation $f\to-f$.
-\begin{figure}[h!]
-\includegraphics[width=0.9\linewidth]{convex_function.pdf}
-\caption{\label{fig:convex}A chord showing convexity of the function $x^4$.} 
-\end{figure}
 
@@
 Any local optimum $x^*$ for a convex optimisation problem is also a global optimum \cite[pp.138-139]{cvxpybook}, however an optimum may not be unique.
+
+\begin{figure}[h!]
+\includegraphics[width=0.9\linewidth]{convex_function.pdf}
+\caption{\label{fig:convex}A chord showing convexity of the function $x^4$.} 
+\end{figure}
 
@@
 
+\subsection*{Author Biography}
+Robert Gowers, Sami Al-Izzi, Timothy Pollington and Roger Hill are PhD students in the Mathematics for Real-World Systems CDT at the University of Warwick.
+Keith Briggs is a senior research mathematician at BT.
+
 \vspace{0.2cm}

### 2017-10-25 minimisePgivenSINR.py
small update on python file

@@ -10,12 +10,16 @@ d_s = 0.5 * (d + d.T)
 G = np.zeros((n,n))
 G = k / d_s ** 3.5
 
-$\delta$ = np.identity(n)
-S = G * $\delta$
+# $\delta$ = np.identity(n)
+δ = np.identity(n)
+# S = G * $\delta$
+S = G * δ
 I = G - S
 
-$\sigma$ = 0.1 * np.ones(n)
-$\gamma$ = 1.0
+# $\sigma$ = 0.1 * np.ones(n)
+σ = 0.1 * np.ones(n)
+# $\gamma$ = 1.0
+γ = 1.0
 Pmax = 1.0
 
 # Define optimisation variable
@@ -27,12 +31,16 @@ obj = cvx.Minimize(
 
 # Define constraints
 constraints = [p >= 0,
-               S * p - $\gamma$ * (I * p + $\sigma$) >= 0,
+               # S * p - $\gamma$ * (I * p + $\sigma$) >= 0,
+               S * p - γ * (I * p + σ) >= 0,
                p <= Pmax]
 
 # Solve problem and print solution
 prob = cvx.Problem(obj, constraints)
 prob.solve()
-print("Solution status = %s"%(prob.status))
-print("Optimal solution = %s"%(prob.value))
-print("Power settings = %s"%(p.value))
+
+print('Solution status = {0}'.format(prob.status))
+print('Optimal solution = {0:.3f}'.format(prob.value))
+if prob.status == 'optimal':
+	for j in range(n):
+		print('Power {0} = {1}'.format(j,p.value[j]))

### 2017-10-25 article_cvxpy.tex
minor uncommitted previous changes
Interieor point method explination

@@
 
-\title{Convex optimisation in communications with \texttt{cvxpy}}
+\title{Communicating with convexity}
 \author{Robert P.~Gowers}%
@@
 If DCP rules can be applied then interior point methods guarantee an optimal solution.
-
+Interior point methods work by applying Newtons algorithm to sequences of equally constrained problems.
+The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality, for more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.
 \section{Example: power minimisation in communications}
@@
 
-%\section{Further applications}
 \subsection*{Acknowledgements}
-We would like to thank S.~Johnson from MathSys and S.~Diamond for helpful discussions.
+We would like to thank S.~Johnson and S.~Diamond for helpful discussions.
 

### 2017-11-03 article_cvxpy.tex
Corrections reccomended by referee

@@
 \subsection{Convex functions}
-%If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}. More formally, for $x,y\in C$ and $\theta\in [0,1]$:
-%\begin{align}
-%\theta x + (1-\theta)y\in C.
-%\end{align}
+If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}. More formally, for $x,y\in C$ and $\theta\in [0,1]$:
+\begin{align}
+\theta x + (1-\theta)y\in C.
+\end{align}
 
@@
 \end{align}
-This means that the function is less than or equal to linear, as shown in Fig.~\ref{fig:convex}. %A concave function can be made convex by the operation $f\to-f$.
+This means that the function is less than or equal to linear, as shown in Fig.~\ref{fig:convex}. A concave function can be made convex by the operation $f\to-f$.
 
@@
 \includegraphics[width=0.9\linewidth]{convex_function.pdf}
-\caption{\label{fig:convex}A chord showing convexity of the function $x^4$.} 
+\caption{\label{fig:convex}The function $f(x)=x^4$ is plotted in blue.
+The convexity of this function can be seen by picking any two values of $x$ and noting that $f(x)$ will always lie below or on the chord connecting these two points.}
 \end{figure}
@@
 The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality, for more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.
+
 \section{Example: power minimisation in communications}
 \noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
-In this problem we are constrained to having a minimum signal-to-interference-plus-noise ratio (SINR) at each receiver; the strength of the desired signal, $S$, relative to the interference power, $I$, plus the background noise, $\sigma$, at a receiver.
+In this problem we are constrained to having a minimum signal-to-interference-plus-noise ratio (SINR or $\gamma$) at each receiver
+\begin{equation}
+\gamma =\frac{S}{I+\sigma}
+\end{equation} 
+where $S$ is the power of the desired signal, $I$ is the interference power and $\sigma$ is the background noise at a receiver.
+
 How can we minimise the total power consumption, $P$, of transmitters, yet achieve this minimum SINR, $\gamma_0$, for all receivers?
 This question is relevant to telecoms companies who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path gain matrix, $G$, background noise level $\sigma$ and a maximum power constraint $P_{\text{max}}$ of each transmitter:
+We formulate the problem with a given square path gain matrix, $G$, background noise level $\sigma$, a maximum power constraint $P_{\text{max}}$ of each transmitter and the fact that all transmitters must have positive power:
 \begin{align*}
@@
 
-The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, while the interference at $i$ is $I_i = \sum_{j\neq k}G_{ij}p_j$. However DCP does not allow division of the optimisation variable $p_i$ so  
+The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, while the interference at $i$ is $I_i = \sum_{j\neq k}G_{ij}p_j$.
+However DCP does not allow division of the optimisation variable $p_i$, as it cannot guarantee curvature, so
 \begin{equation*}
@@
 \end{equation*}
-was rearranged to,
+is rearranged to,
 \begin{equation*}
@@
 For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}.
-Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily incorporated.
+Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily incorporated, whilst remaining within the DCP framework.
 
@@
 \noindent The authors hope that this article shows the utility of \texttt{cvxpy} for simple `toy' problems of real-world relevance.
-We believe it is an invaluable resource for researchers wanting to test the applicability of convex optimisation in new fields.
+$\texttt{cvxpy}$ can handle problems with up to $\sim 10^3$ transmitters, however this takes $\sim 10^{4}-10^{5}\text{ms}$ to run, hence for large real-world problems a faster implementation would likely be required (e.g.
+C++ based library).
+However there is obviously a trade off in terms of ease of understanding with these packages.
 
+We believe that $\texttt{cvxpy}$ is an invaluable resource for researchers wanting to test the applicability of convex optimisation in new fields.
 The module could also be easily incorporated into a course on optimisation, providing students with an accessible environment to practise techniques for convex optimisation.

### 2017-11-09 article_cvxpy.tex
example implementation improved

@@
 \section{Example: power minimisation in communications}
-\noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
+\noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_k$, ($k=1,2,...,n$) and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
 In this problem we are constrained to having a minimum signal-to-interference-plus-noise ratio (SINR or $\gamma$) at each receiver
@@
 
-How can we minimise the total power consumption, $P$, of transmitters, yet achieve this minimum SINR, $\gamma_0$, for all receivers?
+How can we minimise the total power consumption, $P$, of transmitters, yet achieve this minimum SINR, $\gamma_0$, for all $i$ receivers ($i = 1,2,...,m$)?
 This question is relevant to telecoms companies who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path gain matrix, $G$, background noise level $\sigma$, a maximum power constraint $P_{\text{max}}$ of each transmitter and the fact that all transmitters must have positive power:
+We formulate the problem with a given square path gain matrix, $G$, background noise level vector $\sigma$, a maximum power constraint $P_{\text{max}}$ of each transmitter and the fact that all transmitters must have positive power:
 \begin{align*}
-&\underset{p}{\text{minimise}} \quad &&\sum_j p_j\\
-&\text{subject to} \quad &&p_j \leq P_{\max}\\
-& \quad &&p_j \geq 0\\
+&\underset{p}{\text{minimise}} \quad &&\sum_k p_k\\
+&\text{subject to} \quad &&p_k \leq P_{\max}\\
+& \quad &&p_k \geq 0\\
 & \quad &&\gamma_i \geq \gamma_0.&&
@@
 
-The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, while the interference at $i$ is $I_i = \sum_{j\neq k}G_{ij}p_j$.
-However DCP does not allow division of the optimisation variable $p_i$, as it cannot guarantee curvature, so
+Supposing that we want to receive a signal at receiver $i$ from transmitter $k$, we define the recipient matrix, $\delta$, as
+\begin{align*}
+\delta_{ij} = \begin{cases}
+1, \quad j=k\\
+0, \quad j\neq k
+\end{cases},
+\end{align*}
+and our signal potential matrix $\hat{S}$ as $\hat{S} = G*\delta$.  This means that signal received at transmitter $i$ is, $S_i = \hat{S}_{ik}p_k = G_{ik}p_k$.
+% The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, 
+While the interference potential matrix is defined as $\hat{I} = G-\hat{S}$, giving the interference at $i$ is $I_i = (\hat{I}*p)_i = \sum_{j\neq k}G_{ij}p_j$.
+We must note that DCP does not allow division of the optimisation variable $p_i$, as it cannot guarantee curvature, so
 \begin{equation*}
-  \gamma_i \geq \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i}\geq \gamma_0, \quad \forall i
+  \gamma_i \geq \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i} = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j} \geq \gamma_0, \quad \forall i
 \end{equation*}
@@
 \subsection{Path gain}
-\noindent The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$.
+%\noindent The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$.
 Supposing that the desired signal to receiver $i$ is from transmitter $k$, the power received is,
-\begin{equation}
-p_{ik}^{\text{rec}} = G_{ik}p_k.
-\end{equation}
-Denoting the SINR at $i$ by $\gamma_i$, we have
-\begin{equation}
-\gamma_i = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j}
-=\frac{S_i}{\sigma_i+I_i}.
-\end{equation}
-In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$ between them.
+%\begin{equation}
+%p_{ik}^{\text{rec}} = G_{ik}p_k.
+%\end{equation}
+%Denoting the SINR at $i$ by $\gamma_i$, we have
+%\begin{equation}
+%\gamma_i = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j}
+%=\frac{S_i}{\sigma_i+I_i}.
+%\end{equation}
+\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$ between them.
 Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is:
@@
 
+\subsection{Implementation}
+For ease of terminology, we will make a few simplifying assumptions.
+First, we set the number of transmitters equal to the number of receivers, so $n=m$.
+We also pair receiver $i$ to transmitter $k$ such that $i=k$.
+This means that the recipient matrix $\delta$ is the $n\times n$ identity matrix.\\
+
+For paired transmitters and receivers ($k=i$), we randomly sample distances $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.
+For unpaired transmitters and receivers ($k\neq i$), we randomly sample distances $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.\\
+
+We have chosen the background noise vector $\sigma$ as constant for each receiver, with $\sigma_i = 5$.
+
 \subsection{Example code}
-\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below: \lstinputlisting[language=Python,mathescape=true]{minimisePgivenSINR.py}
+\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below: \lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={δ}{$\delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}
 

### 2017-11-09 minimisePgivenSINR.py

@@ -1,46 +1,58 @@
 import cvxpy as cvx
 import numpy as np
 
-# Define variables
-n = 3
-k = 1.0
-d = np.random.rand(n,n)
-d_s = 0.5 * (d + d.T)
+feasibility_count = 0
+total_power = 0
 
-G = np.zeros((n,n))
-G = k / d_s ** 3.5
+for i in range(5000):
+  np.random.seed(i)
 
-# $\delta$ = np.identity(n)
-δ = np.identity(n)
-# S = G * $\delta$
-S = G * δ
-I = G - S
+  # Define variables
+  n = 3 # number of transmitters = number of receivers
+  k = 0.025 # receiver coefficient, assume uniform
+  δ = np.identity(n) # identity matrix
+  d = np.random.rand(n,n) # transmitters placed distance d∈U[0,1] from receivers
+  d_diag = np.random.beta(2,2,size=n)*0.20
+  d = np.tril(d) + np.tril(d, -1).T-np.diag(d)*δ+d_diag*δ # make the matrix symmetric with smaller diagonal elements
+  # print(d)
 
-# $\sigma$ = 0.1 * np.ones(n)
-σ = 0.1 * np.ones(n)
-# $\gamma$ = 1.0
-γ = 1.0
-Pmax = 1.0
+  G = np.zeros((n,n)) # gain matrix G
+  G = k / d ** 3.5
 
-# Define optimisation variable
-p = cvx.Variable(n)
+  # print(G)
 
-# Define objective function
-obj = cvx.Minimize(
-      cvx.sum_entries(p))
+  S = G * δ # desired signal matrix
+  I = G - S # interference matrix
 
-# Define constraints
-constraints = [p >= 0,
-               # S * p - $\gamma$ * (I * p + $\sigma$) >= 0,
-               S * p - γ * (I * p + σ) >= 0,
-               p <= Pmax]
+  σ = 5.0 * np.ones(n)
+  γ = 1.0 # minimimum acceptable SINR
+  Pmax = 1.0 # total power for the n transmitters
 
-# Solve problem and print solution
-prob = cvx.Problem(obj, constraints)
-prob.solve()
+  # Define optimisation variable
+  p = cvx.Variable(n)
 
-print('Solution status = {0}'.format(prob.status))
-print('Optimal solution = {0:.3f}'.format(prob.value))
-if prob.status == 'optimal':
-	for j in range(n):
-		print('Power {0} = {1}'.format(j,p.value[j]))
+  # Define objective function
[…]

### 2017-11-10 article_cvxpy.tex
updated text to be more consistent with code and vice versa

@@
 	\NewsItem{\noindent``Nothing takes place in the world whose meaning is not that of some maximum or minimum.''}
-	\NewsAuthor{Leonard Euler (1707-1783)}
+	\NewsAuthor{Leonhard Euler (1707-1783)}
 
@@
 \begin{equation*}
-  \gamma_i \geq \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i} = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j} \geq \gamma_0, \quad \forall i
+  \gamma_i \geq \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i} = \frac{\hat{S}_{ik}p_k}{\sigma_i+(\hat{I}*p)_i} \geq \gamma_0, \quad \forall i
 \end{equation*}
@@
 \begin{equation*}
-S_i-\gamma_0(\sigma_i + I_i)\geq 0, \quad \forall i
-\end{equation*} which is affine, and hence a DCP function.
+\hat{S}_{ik}p_k-\gamma_0(\sigma_i + (\hat{I}*p)_i)\geq 0, \quad \forall i,
+\end{equation*} 
+which is affine, and hence a DCP function.
 
@@
 \begin{equation}
-G_{ij} = k_i/d_{ij}^\alpha
+G_{ij} = A_i/d_{ij}^\alpha
 \end{equation}
@@
 
-For paired transmitters and receivers ($k=i$), we randomly sample distances $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.
-For unpaired transmitters and receivers ($k\neq i$), we randomly sample distances $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.\\
+All the parameters we will take as dimensionless to give simple numbers to work with.
+The maximum available power, $P_{\text{max}}$ is set to 1.
+We have chosen the background noise vector $\sigma$ as constant for each receiver, with $\sigma_i = 5$.
+Similarly, the receiver coefficient $A$ was set to $0.025$ for each receiver.
+\\
 
-We have chosen the background noise vector $\sigma$ as constant for each receiver, with $\sigma_i = 5$.
+To generate the gain matrix $G$, we randomly sample distances from a given distribution.
+For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.
+For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.\\
 
 \subsection{Example code}
-\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below: \lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={δ}{$\delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}
+\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below.
+For the random seed of 100 given, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
+Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\sim0.4$.
+
+\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={δ}{$\delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}
 

### 2017-11-10 minimisePgivenSINR.py

@@ -1,58 +1,46 @@
 import cvxpy as cvx
 import numpy as np
 
-feasibility_count = 0
-total_power = 0
+np.random.seed(100)
 
-for i in range(5000):
-  np.random.seed(i)
+# Define variables
+n = 3 # number of transmitters = receivers
+A = 0.025 # uniform receiver coefficient
+δ = np.identity(n) # identity matrix
+# unwanted transmitters d∈U[0,1] from receivers
+d_unpair = np.random.rand(n,n)
+# desired transmitters d∈0.2B[2,2] from receivers
+d_pair = np.random.beta(2,2,size=n)*0.20 
+ # make the matrix symmetric
+d = np.tril(d_unpair) + np.tril(d_unpair, -1).T-np.diag(d_unpair)*δ+d_pair*δ
 
-  # Define variables
-  n = 3 # number of transmitters = number of receivers
-  k = 0.025 # receiver coefficient, assume uniform
-  δ = np.identity(n) # identity matrix
-  d = np.random.rand(n,n) # transmitters placed distance d∈U[0,1] from receivers
-  d_diag = np.random.beta(2,2,size=n)*0.20
-  d = np.tril(d) + np.tril(d, -1).T-np.diag(d)*δ+d_diag*δ # make the matrix symmetric with smaller diagonal elements
-  # print(d)
+G = np.zeros((n,n)) # gain matrix G
+G = A / d ** 3.5
+S_hat = G * δ # signal potential matrix
+I_hat = G - S_hat # interference potential matrix
 
-  G = np.zeros((n,n)) # gain matrix G
-  G = k / d ** 3.5
+σ = 5.0 * np.ones(n)
+γ = 1.0 # minimimum acceptable SINR
+Pmax = 1.0 # total power for each transmitter
 
-  # print(G)
+# Define optimisation variable as the transmitter powers
+p = cvx.Variable(n)
 
-  S = G * δ # desired signal matrix
-  I = G - S # interference matrix
+# Define objective function as the total power
+obj = cvx.Minimize(cvx.sum_entries(p))
 
-  σ = 5.0 * np.ones(n)
-  γ = 1.0 # minimimum acceptable SINR
-  Pmax = 1.0 # total power for the n transmitters
+# Define constraints
+constraints = [p >= 0,
+              S_hat * p - γ * (I_hat * p + σ) >= 0,
+              p <= Pmax]
 
-  # Define optimisation variable
-  p = cvx.Variable(n)
+# Solve problem and print solution
[…]

### 2017-11-13 article_cvxpy.tex
added distance distribution plot

@@
 For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.
-For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.\\
+For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.
+This is illustrated in Figure \ref{fig:dist}.
+
+\begin{figure}[h!]
+\includegraphics[width=0.9\linewidth]{distance_distributions.pdf}
+\caption{\label{fig:dist}The distance between unpaired transmitters and receivers has a higher variance than paired ones, but on average the unpaired distances are expected to be greater.} 
+\end{figure}
 

### 2017-11-13 distance_distribution_plot.py

@@ -1,0 +1,19 @@
+import numpy as np
+import matplotlib.pylab as plt
+from matplotlib.backends.backend_pdf import PdfPages
+from scipy.stats import beta
+
+a = 2
+b = 2
+x = np.linspace(0,1,1000)
+u = np.ones(len(x))
+u[0] = 0
+u[-1] = 0
+
+with PdfPages('distance_distributions.pdf') as pdf:
+	plt.plot(0.2*x,5*beta.pdf(x, a, b), label="Paired Distribution")
+	plt.plot(x,u, label="Unpaired Distribution")
+	plt.xlabel("Distance, $d$")
+	plt.ylabel("Probability Density")
+	plt.legend(loc="best")
+	pdf.savefig(bbox_inches="tight")

### 2017-11-22 article_cvxpy.tex
added waterfilling

@@
+% edited Keith Briggs 2017-11-16
+% latexmk -pdf article_cvxpy_2017-11-16 && e article_cvxpy_2017-11-16.pdf &
+
 \documentclass[twocolumn,secnumarabic,amssymb, nobibnotes, aps, prl,superscriptaddress]{revtex4-1}
@@
 }
+
+\medmuskip=1mu plus 0.5mu minus 1.5mu
+\def\cpp{{C\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}}
+
 \lstset{style=mystyle}
@@
 \email{keith.briggs@bt.com}
-\affiliation{BT, Adastral Park}
+\affiliation{BT Research, Adastral Park, Suffolk}
 %\affiliation{r.gowers@warwick.ac.uk}
@@
 \section{Introduction}
-\noindent Convexity is an important property in optimisation.
-This is because if a problem is convex then the task of finding a global minimum is reduced to that of finding a local minimum.
-The importance of finding these minima efficiently in science and engineering has driven the development of software packages, such as \texttt{cvxpy}.
+\noindent Convexity is a fundamentally important property in optimisation.
+Roughly speaking, an optimisation is convex if its objective function is convex, as well the set of points satifying any constraints, and in such cases the task of finding a global minimum is reduced to that of finding a local minimum.
+The importance of finding these minima efficiently in science and engineering applications has driven the development of software packages, such as \texttt{cvxpy} from the group of Stephen Boyd at Stanford University.
 
-Here we show that an interesting problem in communications has a convex formulation that can be easily implemented computationally using the \texttt{cvxpy} \textit{Python} module.
-This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering.
-First let us introduce what convexity means.
+Here we show that an realistic problem in communications has a convex formulation which can be easily implemented computationally using the \texttt{cvxpy}, and coded in Python.
+This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering, and has the very useful advantage that the program structure closely mirrors the mathematical description of the problem.
+First let us define properly what convexity means.
 
 \subsection{Convex functions}
-If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}. More formally, for $x,y\in C$ and $\theta\in [0,1]$:
+\noindent{}If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}.
+More formally, for $x,y\in C$ and $\theta\in [0,1]$:
 \begin{align}
@@
 
-\noindent A function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$, is \textit{convex} if $\forall x,y\in \textbf{dom} f$ and $0 \leq \theta \leq 1$ \cite[p.67]{cvxpybook}:
+\noindent A function $f$, where $f:\mathbb{R}^n \rightarrow \mathbb{R}$, is \textit{convex} if $\forall x,y\in \textbf{dom} f$ and $0 \leqslant \theta \leqslant 1$ \cite[p.67]{cvxpybook}:
 \begin{align}
-f(\theta x + (1-\theta)y) \leq \theta f(x)+(1-\theta)f(y).
+f(\theta x + (1-\theta)y) \leqslant \theta f(x)+(1-\theta)f(y).
 \end{align}
-This means that the function is less than or equal to linear, as shown in Fig.~\ref{fig:convex}. A concave function can be made convex by the operation $f\to-f$.
+This means that the function value at intermediate points of any interval is less than or equal to an affine function interpolating the end points of the interval, as shown in Fig.~\ref{fig:convex}.
+A concave function can be made convex by the operation $f\to-f$.
 
@@
 \item a convex \textit{objective function} $f_0(x)$,
-\item $m$ convex \textit{inequality constraint functions} $f_i(x)$,
-\item $k$ convex \textit{equality constraint functions} $g_j(x)$, 
+\item $m\geqslant0$ convex \textit{inequality constraint functions} $f_i(x)$,
+\item $k\geqslant0$ convex \textit{equality constraint functions} $g_j(x)$, 
 \end{itemize}
@@
 &\text{minimise } && f_0(x) & \nonumber &\\
-&\text{subject to } && f_i(x) \leq 0,\quad & i\in \{1,..,m\}\nonumber &\\
+&\text{subject to } && f_i(x) \leqslant 0,\quad & i\in \{1,..,m\}\nonumber &\\
 & && g_{j}(x)=0,\quad & j\in \{1,...,k\} &.
@@
 \subsection{Disciplined convex programming}
-\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for \textit{Python}\cite{cvxpy}.
+\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy}.
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
@@
 If DCP rules can be applied then interior point methods guarantee an optimal solution.
-Interior point methods work by applying Newtons algorithm to sequences of equally constrained problems.
+%Interior point methods work by applying Newton's algorithm to sequences of equally constrained problems. Is it right that Newton's method is used???
  The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality, for more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.
 
-\section{Example: power minimisation in communications}
-\noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_k$, ($k=1,2,...,n$) and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}.
-In this problem we are constrained to having a minimum signal-to-interference-plus-noise ratio (SINR or $\gamma$) at each receiver
+ \section{Example 1: water-filling}
+
+ One of the simplest problems to solve in communications with convex optimisation is the classic \textit{water-filling} problem.
+This is where a total power $P$ is to be assigned to $n$ different communications channels, with the objective of maximising the total communication rate.
+The communication rate of the $i$th channel, $r_i$ is given by \citep[p.245]{cvxpybook},
+ \begin{align}
+  r_i = \log(x_i+\alpha_i),
+ \end{align}
+ where $x_i$ is the power allocated to the $i$th channel and $\alpha_i$ is the floor above the baseline at which power can be added to the channel.
+This can be seen in Figure \ref{fig:waterfilling} as being analogous to filling an uneven basin to a constant level (hence the name \textit{water-filling}).
+
+ Noting that all power allocations must be non-negative, the optimisation problem can therefore be formulated as,
+ \begin{align}
+\text{minimise} \quad  -&\sum_{i=1}^{n} \log(x_i+\alpha_i) \nonumber \\
+\text{subject to} \quad &x_i \geq 0, \quad \forall i \nonumber \\
+&\sum_{i=1}^{n}x_i = P.
+ \end{align}
+ This is a convex problem since $-\log(x_i+\alpha_i)$ has positive curvature within the domain $x_i \geq 0$, and all the constraints are affine and therefore convex.
+
+\subsection{Implementation}
+We decided to solve the water-filling problem using \texttt{cvxpy} with $n=3$ channels and $(\alpha_1,\alpha_2,\alpha_3) = (0.8,1.0,1.2)$.
+For simplicity we chose a dimensionless total power $P=1$.
+Using these parameters, the maximum communication rate is, $\sum_{i=1}^{n}r_i = 0.863$, which is achieved with power allocations $(x_1,x_2,x_3) = (8/15,5/15,2/15)$.
+This is the solution shown in Figure \ref{fig:waterfilling}.
+
+\subsection{Example Code}
+\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below with the parameters chosen above.
+With an ordinary commercially available laptop, the time taken to execute the code was around 4ms.
+\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={α}{$\alpha$}1 ]{waterfilling.py}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1.0\linewidth]{water_filling_plot.pdf}
+\caption{The greatest amount of power, $x$, is allocated to the channel with the lowest $\alpha$.}
+\label{fig:waterfilling}
+\end{figure}
+
+\section{Example 2: power minimisation in communications}
+\noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_k$, ($k=1,2,...,n$) and $m$ receivers, all in two-dimensional Euclidean space \cite{shannon1949}.
+At receiver $i$ there is a power $S_i$ of the desired signal, and an interference power $I_i$ from undesired signals, and a background noise $\sigma$.
+In this problem we are constrained to having a specified minimum signal-to-interference-plus-noise ratio (SINR or $\gamma$) at each receiver
 \begin{equation}
-\gamma =\frac{S}{I+\sigma}
+\gamma_i =\frac{S_i}{I_i+\sigma}.
 \end{equation}
-where $S$ is the power of the desired signal, $I$ is the interference power and $\sigma$ is the background noise at a receiver.
 
 How can we minimise the total power consumption, $P$, of transmitters, yet achieve this minimum SINR, $\gamma_0$, for all $i$ receivers ($i = 1,2,...,m$)?
-This question is relevant to telecoms companies who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path gain matrix, $G$, background noise level vector $\sigma$, a maximum power constraint $P_{\text{max}}$ of each transmitter and the fact that all transmitters must have positive power:
+This question is relevant to telecom companies who want to offer a service at a minimum quality standard.
+We formulate the problem with a given square path-gain matrix, $G$, background noise level vector $\sigma$, a maximum power constraint $P_{\text{max}}$ of each transmitter and the fact that all transmitters must be supplied with positive power:
 \begin{align*}
 &\underset{p}{\text{minimise}} \quad &&\sum_k p_k\\
-&\text{subject to} \quad &&p_k \leq P_{\max}\\
-& \quad &&p_k \geq 0\\
-& \quad &&\gamma_i \geq \gamma_0.&&
+&\text{subject to} \quad &&p_k \leqslant P_{\max}\\
+& \quad &&p_k \geqslant 0\\
+& \quad &&\gamma_i \geqslant \gamma_0.&&
 \end{align*}
 
-Supposing that we want to receive a signal at receiver $i$ from transmitter $k$, we define the recipient matrix, $\delta$, as
+Supposing that we want to receive a signal at receiver $i$ from transmitter $k$, we define the recipient matrix, $\Delta$, as
 \begin{align*}
-\delta_{ij} = \begin{cases}
+\Delta_{ij} = \begin{cases}
 1, \quad j=k\\
@@
 \end{align*}
-and our signal potential matrix $\hat{S}$ as $\hat{S} = G*\delta$.  This means that signal received at transmitter $i$ is, $S_i = \hat{S}_{ik}p_k = G_{ik}p_k$.
+and our signal potential matrix $\hat{S}$ as $\hat{S} = G\Delta$.  This means that signal received at transmitter $i$ is $S_i = \hat{S}_{ik}p_k = G_{ik}p_k$.
 % The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, 
@@
 \begin{equation*}
-  \gamma_i \geq \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i} = \frac{\hat{S}_{ik}p_k}{\sigma_i+(\hat{I}*p)_i} \geq \gamma_0, \quad \forall i
+  \gamma_i \geqslant \gamma_0\Longleftrightarrow  \frac{S_i}{\sigma_i + I_i} = \frac{\hat{S}_{ik}p_k}{\sigma_i+(\hat{I}*p)_i} \geqslant \gamma_0, \quad \forall i
 \end{equation*}
-is rearranged to,
+is rearranged to
 \begin{equation*}
-\hat{S}_{ik}p_k-\gamma_0(\sigma_i + (\hat{I}*p)_i)\geq 0, \quad \forall i,
+\hat{S}_{ik}p_k-\gamma_0(\sigma_i + (\hat{I}*p)_i)\geqslant 0, \quad \forall i,
 \end{equation*} 
@@
 %\end{equation}
-\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$ between them.
+\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance $d_{ij}$ between them.
 Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is:
@@
 We also pair receiver $i$ to transmitter $k$ such that $i=k$.
-This means that the recipient matrix $\delta$ is the $n\times n$ identity matrix.\\
+This means that the recipient matrix $\Delta$ is the $n\times n$ identity matrix.
 
@@
 \subsection{Example code}
-\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below.
 For the random seed of 100 given, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
+The time taken to find this solution was around 3ms.
 Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\sim0.4$.
 
-\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={δ}{$\delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}
+\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={Δ}{$\Delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}
 
@@
 \noindent The authors hope that this article shows the utility of \texttt{cvxpy} for simple `toy' problems of real-world relevance.
-$\texttt{cvxpy}$ can handle problems with up to $\sim 10^3$ transmitters, however this takes $\sim 10^{4}-10^{5}\text{ms}$ to run, hence for large real-world problems a faster implementation would likely be required (e.g.
-C++ based library).
-However there is obviously a trade off in terms of ease of understanding with these packages.
+$\texttt{cvxpy}$ can handle problems with up to $\sim 10^3$ transmitters, however this takes $\sim 10^{4}-10^{5}\text{ms}$ to run, hence for large real-world problems a faster implementation would likely be required (e.g., a \cpp-based library).
+However, there is obviously a trade-off in terms of ease of understanding with these packages.
 
@@
 The module could also be easily incorporated into a course on optimisation, providing students with an accessible environment to practise techniques for convex optimisation.
-Full code for other communication examples can be found at https://github.com/cvxgrp/cvxpy/\\tree/master/examples/communications.
+Full code for other communication examples can be found at \url{https://github.com/cvxgrp/cvxpy/\\tree/master/examples/communications}.
 
@@
 \subsection*{Acknowledgements}
-We would like to thank S.~Johnson and S.~Diamond for helpful discussions.
+\noindent{}We would like to thank S.~Johnson and S.~Diamond for helpful discussions.
 
 \subsection*{Author Biography}
-Robert Gowers, Sami Al-Izzi, Timothy Pollington and Roger Hill are PhD students in the Mathematics for Real-World Systems CDT at the University of Warwick.
-Keith Briggs is a senior research mathematician at BT.
+\noindent{}Robert Gowers, Sami Al-Izzi, Timothy Pollington, and Roger Hill are PhD students in the Mathematics for Real-World Systems CDT at the University of Warwick.
+Keith Briggs is a esearch mathematician at BT.
 

### 2017-11-22 minimisePgivenSINR.py

@@ -6,17 +6,17 @@ np.random.seed(100)
 # Define variables
 n = 3 # number of transmitters = receivers
 A = 0.025 # uniform receiver coefficient
-δ = np.identity(n) # identity matrix
+Δ = np.identity(n) # identity matrix
 # unwanted transmitters d∈U[0,1] from receivers
 d_unpair = np.random.rand(n,n)
 # desired transmitters d∈0.2B[2,2] from receivers
 d_pair = np.random.beta(2,2,size=n)*0.20 
  # make the matrix symmetric
-d = np.tril(d_unpair) + np.tril(d_unpair, -1).T-np.diag(d_unpair)*δ+d_pair*δ
+d = np.tril(d_unpair) + np.tril(d_unpair, -1).T-np.diag(d_unpair)*Δ+d_pair*Δ
 
 G = np.zeros((n,n)) # gain matrix G
 G = A / d ** 3.5
-S_hat = G * δ # signal potential matrix
+S_hat = G * Δ # signal potential matrix
 I_hat = G - S_hat # interference potential matrix
 
 σ = 5.0 * np.ones(n)

### 2017-11-22 waterfilling.py

@@ -1,7 +1,11 @@
-# Define variable (x) & parameter (a) with total power to allocate (sum_x) and number of channels (n).
-x = cvx.Variable(n)
-alpha = cvx.Parameter(n,sign='positive')
-alpha.value = a
+import cvxpy as cvx
+import numpy as np
+
+n = 3 # number of channels
+P = 1 # total power available to allocate
+x = cvx.Variable(n) # optimisation variable x
+α = cvx.Parameter(n,sign='positive') # baseline paramter α 
+α.value = [0.8,1.0,1.2]
 
 # Define objective function
 obj = cvx.Maximize(cvx.sum_entries
@@ -10,8 +14,16 @@ obj = cvx.Maximize(cvx.sum_entries
 
 # Define constraints
 constraints = [x >= 0,
-               cvx.sum_entries(x) - sum_x ==0]
+               cvx.sum_entries(x) - P ==0]
 
 # Solve problem
 prob = cvx.Problem(obj, constraints)
 prob.solve()
+
+powers = np.asarray(x.value)
+
+print('Solution status = {0}'.format(prob.status))
+print('Optimal solution = {0:.3f}'.format(prob.value))
+if prob.status == 'optimal':
+  for j in range(n):
+  	print('Power {0} = {1:.3f}'.format(j,powers[j][0]))

### 2017-11-23 article_cvxpy.tex
water-filling plot updated

@@
+% edited Keith Briggs 2017-11-23
 % edited Keith Briggs 2017-11-16
-% latexmk -pdf article_cvxpy_2017-11-16 && e article_cvxpy_2017-11-16.pdf &
+% latexmk -pdf article_cvxpy && e article_cvxpy.pdf &
 
@@
 
- One of the simplest problems to solve in communications with convex optimisation is the classic \textit{water-filling} problem.
-This is where a total power $P$ is to be assigned to $n$ different communications channels, with the objective of maximising the total communication rate.
-The communication rate of the $i$th channel, $r_i$ is given by \citep[p.245]{cvxpybook},
+\noindent{}One of the simplest problems to solve in communications with convex optimisation is the classic \textit{water-filling} problem.
+Here a total power $P$ is to be assigned to $n$ different communications channels, with the objective of maximising the total communication rate.
+By Shannon's theorem \citep[p.245]{cvxpybook}, an upper bound for the rate is given by $\log(1+x_i/\alpha_i)$, where $x_i$ be the power allocated to the $i$th channel and $\alpha_i$ is the noise power in that channel.
+This can be written as $\log(\alpha_i+x_i)-\log(\alpha_i)$ and the constants $\log(\alpha_i)$ disregarded for the purposes of maximization, and thus the communication rate $r_i$ of the $i$th channel is given by
  \begin{align}
-  r_i = \log(x_i+\alpha_i),
+  r_i = \log(x_i+\alpha_i).
  \end{align}
- where $x_i$ is the power allocated to the $i$th channel and $\alpha_i$ is the floor above the baseline at which power can be added to the channel.
-This can be seen in Figure \ref{fig:waterfilling} as being analogous to filling an uneven basin to a constant level (hence the name \textit{water-filling}).
+This can be seen in Figure~\ref{fig:waterfilling} as being analogous to filling an uneven basin to a constant level (hence the name \textit{water-filling}).
 
@@
 \text{minimise} \quad  -&\sum_{i=1}^{n} \log(x_i+\alpha_i) \nonumber \\
-\text{subject to} \quad &x_i \geq 0, \quad \forall i \nonumber \\
+\text{subject to} \quad &x_i \geqslant 0, \quad \forall i \nonumber \\
 &\sum_{i=1}^{n}x_i = P.
  \end{align}
- This is a convex problem since $-\log(x_i+\alpha_i)$ has positive curvature within the domain $x_i \geq 0$, and all the constraints are affine and therefore convex.
+This is a convex problem since $-\log(x_i+\alpha_i)$ has positive curvature within the domain $x_i \geqslant 0$, and all the constraints are affine and therefore convex.
 
 \subsection{Implementation}
-We decided to solve the water-filling problem using \texttt{cvxpy} with $n=3$ channels and $(\alpha_1,\alpha_2,\alpha_3) = (0.8,1.0,1.2)$.
+\noindent We decided to solve the water-filling problem using \texttt{cvxpy} with $n=3$ channels and $(\alpha_1,\alpha_2,\alpha_3) = (0.8,1.0,1.2)$.
 For simplicity we chose a dimensionless total power $P=1$.
 Using these parameters, the maximum communication rate is, $\sum_{i=1}^{n}r_i = 0.863$, which is achieved with power allocations $(x_1,x_2,x_3) = (8/15,5/15,2/15)$.
-This is the solution shown in Figure \ref{fig:waterfilling}.
+This is the solution shown in Figure~\ref{fig:waterfilling}.
 
@@
 \includegraphics[width=1.0\linewidth]{water_filling_plot.pdf}
-\caption{The greatest amount of power, $x$, is allocated to the channel with the lowest $\alpha$.}
+\caption{The optimal solution to the water-filling problem allocates the greatest amount of power, $x$, to the channel with the lowest noise power, $\alpha$.}
 \label{fig:waterfilling}
@@
 \subsection{Implementation}
-For ease of terminology, we will make a few simplifying assumptions.
+\noindent For ease of terminology, we will make a few simplifying assumptions.
 First, we set the number of transmitters equal to the number of receivers, so $n=m$.
@@
 For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.
-This is illustrated in Figure \ref{fig:dist}.
+This is illustrated in Figure~\ref{fig:dist}.
 
@@
 \subsection{Example code}
-For the random seed of 100 given, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
+\noindent For the random seed of 100 given, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
 The time taken to find this solution was around 3ms.

### 2017-11-23 water_filling_plot.py

@@ -1,0 +1,49 @@
+%PDF-1.4
+% Ǽ
+1 0 obj
+<< /Pages 2 0 R /Type /Catalog >>
+endobj
+8 0 obj
+<< /Pattern 5 0 R /Shading 6 0 R /XObject 7 0 R /Font 3 0 R
+/ExtGState 4 0 R /ProcSet [ /PDF /Text /ImageB /ImageC /ImageI ] >>
+endobj
+3 0 obj
+<< >>
+endobj
+4 0 obj
+<< >>
+endobj
+5 0 obj
+<< >>
+endobj
+6 0 obj
+<< >>
+endobj
+7 0 obj
+<< >>
+endobj
+2 0 obj
+<< /Kids [ ] /Count 0 /Type /Pages >>
+endobj
+9 0 obj
+<< /Creator (matplotlib 2.0.2, http://matplotlib.org)
+/Producer (matplotlib pdf backend) /CreationDate (D:20171123162604+01'00')
+>>
+endobj
+xref
+0 10
+0000000000 65535 f 
+0000000016 00000 n 
+0000000313 00000 n 
+0000000208 00000 n 
+0000000229 00000 n 
+0000000250 00000 n 
+0000000271 00000 n 
+0000000292 00000 n 
+0000000065 00000 n 
+0000000366 00000 n 
+trailer
+<< /Info 9 0 R /Size 10 /Root 1 0 R >>
+startxref
+513
+%%EOF

### 2017-11-23 waterfilling.py

@@ -4,7 +4,7 @@ import numpy as np
 n = 3 # number of channels
 P = 1 # total power available to allocate
 x = cvx.Variable(n) # optimisation variable x
-α = cvx.Parameter(n,sign='positive') # baseline paramter α 
+α = cvx.Parameter(n,sign='positive') # baseline parameter α 
 α.value = [0.8,1.0,1.2]
 
 # Define objective function
@@ -19,7 +19,6 @@ constraints = [x >= 0,
 # Solve problem
 prob = cvx.Problem(obj, constraints)
 prob.solve()
-
 powers = np.asarray(x.value)
 
 print('Solution status = {0}'.format(prob.status))

### 2017-11-23 waterfilling_plot.py

@@ -1,0 +1,29 @@
+import matplotlib
+import matplotlib.pylab as plt
+import numpy as np
+from matplotlib.backends.backend_pdf import PdfPages
+
+matplotlib.rcParams.update({'font.size': 14})
+n=3
+α = np.array([0.8,1.0,1.2])
+X = np.array([8/15,5/15,2/15])
+with PdfPages('water_filling_plot.pdf') as pdf:
+	axis = np.arange(0.5,n+1.5,1)
+	index = axis+0.5
+	# X = np.asarray(x).flatten()
+	Y = α + X
+
+	# to include the last data point as a step, we need to repeat it
+	A = np.concatenate((α,[α[-1]]))
+	X = np.concatenate((X,[X[-1]]))
+	Y = np.concatenate((Y,[Y[-1]]))
+
+	plt.xticks(index)
+	plt.xlim(0.5,n+0.5)
+	plt.ylim(0,1.5)
+	plt.step(axis,A,where='post',label =r'$\alpha$',lw=2)
+	plt.step(axis,Y,where='post',label=r'$\alpha + x$',lw=2)
+	plt.legend(loc='lower right')
+	plt.xlabel('Channel Number')
+	plt.ylabel('Power Level')
+	pdf.savefig(bbox_inches='tight')

### 2017-11-24 article_cvxpy.tex
draft overall updated

@@
 
-Here we show that an realistic problem in communications has a convex formulation which can be easily implemented computationally using the \texttt{cvxpy}, and coded in Python.
+Here we show that real-world problems in communications have convex formulations which can be easily implemented computationally using \texttt{cvxpy}, and coded in Python.
 This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering, and has the very useful advantage that the program structure closely mirrors the mathematical description of the problem.
@@
 %Interior point methods work by applying Newton's algorithm to sequences of equally constrained problems. Is it right that Newton's method is used???
- The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality, for more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.
+ The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality.
+For more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.
 
@@
 Here a total power $P$ is to be assigned to $n$ different communications channels, with the objective of maximising the total communication rate.
-By Shannon's theorem \citep[p.245]{cvxpybook}, an upper bound for the rate is given by $\log(1+x_i/\alpha_i)$, where $x_i$ be the power allocated to the $i$th channel and $\alpha_i$ is the noise power in that channel.
-This can be written as $\log(\alpha_i+x_i)-\log(\alpha_i)$ and the constants $\log(\alpha_i)$ disregarded for the purposes of maximization, and thus the communication rate $r_i$ of the $i$th channel is given by
+By Shannon's theorem \citep[p.245]{cvxpybook}, an upper bound for the rate is given by $\log(1+x_i/\alpha_i)$, where $x_i$ is the power allocated to the $i$th channel and $\alpha_i$ is the noise power in that channel.
+This can be written as $\log(\alpha_i+x_i)-\log(\alpha_i)$ and the constants $\log(\alpha_i)$ are disregarded for the purposes of maximization.
+Thus the communication rate, $r_i$, of the $i$th channel without the constant term is given by,
  \begin{align}
@@
 \noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_k$, ($k=1,2,...,n$) and $m$ receivers, all in two-dimensional Euclidean space \cite{shannon1949}.
-At receiver $i$ there is a power $S_i$ of the desired signal, and an interference power $I_i$ from undesired signals, and a background noise $\sigma$.
-In this problem we are constrained to having a specified minimum signal-to-interference-plus-noise ratio (SINR or $\gamma$) at each receiver
+At receiver $i$ there is a power $S_i$ of the desired signal, an interference power $I_i$ from undesired signals, and a background noise $\sigma$.
+In this problem we are constrained to having a specified minimum signal-to-interference-plus-noise ratio (SINR or $\gamma_0$) at each receiver, with the SINR at receiver $i$ given by,
 \begin{equation}
@@
 
-How can we minimise the total power consumption, $P$, of transmitters, yet achieve this minimum SINR, $\gamma_0$, for all $i$ receivers ($i = 1,2,...,m$)?
+How can we minimise the total power consumption, $P$, of the transmitters, yet achieve this minimum SINR, $\gamma_0$, for all $i$ receivers ($i = 1,2,...,m$)?
 This question is relevant to telecom companies who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path-gain matrix, $G$, background noise level vector $\sigma$, a maximum power constraint $P_{\text{max}}$ of each transmitter and the fact that all transmitters must be supplied with positive power:
+We formulate the problem with a given square path-gain matrix, $G$, background noise level vector, $\sigma$, a maximum power constraint, $P_{\text{max}}$, of each transmitter and the fact that all transmitters must be supplied with positive power:
 \begin{align*}
@@
 While the interference potential matrix is defined as $\hat{I} = G-\hat{S}$, giving the interference at $i$ is $I_i = (\hat{I}*p)_i = \sum_{j\neq k}G_{ij}p_j$.
-We must note that DCP does not allow division of the optimisation variable $p_i$, as it cannot guarantee curvature, so
+We must note that DCP does not allow division of the optimisation variable, $p_i$, as it cannot guarantee curvature, so
 \begin{equation*}
@@
 \subsection{Path gain}
-%\noindent The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$.
-Supposing that the desired signal to receiver $i$ is from transmitter $k$, the power received is,
-%\begin{equation}
-%p_{ik}^{\text{rec}} = G_{ik}p_k.
-%\end{equation}
-%Denoting the SINR at $i$ by $\gamma_i$, we have
-%\begin{equation}
-%\gamma_i = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j}
-%=\frac{S_i}{\sigma_i+I_i}.
-%\end{equation}
 \noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance $d_{ij}$ between them.
-Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is:
+Assuming isotropic propagation from each transmitter, given a pathloss coefficient $\alpha$ and a proportionality constant $A_i$ specific to receiver $i$, the fraction of power from $j$ that reaches $i$ is,
 \begin{equation}
-G_{ij} = A_i/d_{ij}^\alpha
+G_{ij} = A_i/d_{ij}^\alpha.
 \end{equation}
-where $\alpha$ is the pathloss coefficient and $k$ is a proportionality constant specific to the receiver $i$.
 For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}.
@@
 
+\subsection{Example code}
+\noindent For the random seed of 100 shown in the example code, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
+The time taken to find this solution was around 3ms.
+Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\sim0.4$.
+
 \begin{figure}[h!]
@@
 \end{figure}
-
-\subsection{Example code}
-\noindent For the random seed of 100 given, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
-The time taken to find this solution was around 3ms.
-Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\sim0.4$.
 
@@
 The module could also be easily incorporated into a course on optimisation, providing students with an accessible environment to practise techniques for convex optimisation.
-Full code for other communication examples can be found at \url{https://github.com/cvxgrp/cvxpy/\\tree/master/examples/communications}.
-
-%While all problems that can be written in DCP are convex, not all convex problems of interest can be written in DCP.
-Over time, the library of available DCP functions in \texttt{cvxpy} has grown, increasing the scope of convex optimisation problems that \texttt{cvxpy} can solve.
-This expansion of scope of \texttt{cvxpy} is ongoing, with version 1.0 under development and expected in the near future.
-
-%\section{Further Work}
-%While many problems are convex, others fall into a similar category of being \textit{quasi-convex}.
-A quasi-convex function $f$ is one for which $\textbf{dom} f$ and every sublevel set of $f$ is convex.
-An example of this is shown in Figure [?].
-Quasi-convex problems cannot be solved directly using convex optimisation solvers, however the feasibility of a sublevel set can be checked.
-This feasibility check can be used as a bisection method to find the solution.
-A more thorough discussion of quasi-convex problems can be found in \cite{cvxpybook}chapter?.
+Full code for other communication examples can be found at \url{https://github.com/cvxgrp/cvxpy/tree/master/examples/communications}.
 
@@
 \noindent{}Robert Gowers, Sami Al-Izzi, Timothy Pollington, and Roger Hill are PhD students in the Mathematics for Real-World Systems CDT at the University of Warwick.
-Keith Briggs is a esearch mathematician at BT.
+Keith Briggs is a research mathematician at BT.
 

### 2017-12-01 article_cvxpy.tex
Changes suggested by referee

@@
 \subsection{Convex functions}
-\noindent{}If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}.
+\noindent{}If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also be in $C$ \cite[p.23]{cvxpybook}.
 More formally, for $x,y\in C$ and $\theta\in [0,1]$:
@@
 \subsection{Disciplined convex programming}
-\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy}.
+\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy} (all example code is given for Python $3.0$).
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
@@
  \end{align}
-This can be seen in Figure~\ref{fig:waterfilling} as being analogous to filling an uneven basin to a constant level (hence the name \textit{water-filling}).
 
@@
 Using these parameters, the maximum communication rate is, $\sum_{i=1}^{n}r_i = 0.863$, which is achieved with power allocations $(x_1,x_2,x_3) = (8/15,5/15,2/15)$.
-This is the solution shown in Figure~\ref{fig:waterfilling}.
+This solution is shown in Figure~\ref{fig:waterfilling}, and can be seen as being analogous to filling an uneven basin to a constant level (hence the name \textit{water-filling}).
 
@@
 With an ordinary commercially available laptop, the time taken to execute the code was around 4ms.
+Note that the code is a little different in formulation from the text in that it maximises the positive sum of $x_i$ rather than minimising the negative.
+The total power constraint is also rearranged.
 \lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={α}{$\alpha$}1 ]{waterfilling.py}
@@
 \noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_k$, ($k=1,2,...,n$) and $m$ receivers, all in two-dimensional Euclidean space \cite{shannon1949}.
-At receiver $i$ there is a power $S_i$ of the desired signal, an interference power $I_i$ from undesired signals, and a background noise $\sigma$.
+At receiver $i$ there is a power $S_i$ of the desired signal, an interference power $I_i$ from undesired signals, and a background noise $\sigma_i$.
 In this problem we are constrained to having a specified minimum signal-to-interference-plus-noise ratio (SINR or $\gamma_0$) at each receiver, with the SINR at receiver $i$ given by,
 \begin{equation}
-\gamma_i =\frac{S_i}{I_i+\sigma}.
+\gamma_i =\frac{S_i}{I_i+\sigma_i}.
 \end{equation}
@@
 % The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, 
-While the interference potential matrix is defined as $\hat{I} = G-\hat{S}$, giving the interference at $i$ is $I_i = (\hat{I}*p)_i = \sum_{j\neq k}G_{ij}p_j$.
+While the interference potential matrix is defined as $\hat{I} = G-\hat{S}$, giving the interference at $i$ as $I_i = (\hat{I}*p)_i = \sum_{j\neq k}G_{ij}p_j$.
 We must note that DCP does not allow division of the optimisation variable, $p_i$, as it cannot guarantee curvature, so
@@
 %\section{Links \& references}
+\bibliographystyle{ieeetr}
 \bibliography{articleBib}
-\bibliographystyle{plain}
 

### 2017-12-01 article_cvxpy.tex
minor edits to python version, waterfilling and sigma

@@
 \subsection{Disciplined convex programming}
-\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy} (all example code is given for Python $3.0$).
+\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy} (all example code is given for Python 3).
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
@@
 \subsection{Implementation}
-\noindent We decided to solve the water-filling problem using \texttt{cvxpy} with $n=3$ channels and $(\alpha_1,\alpha_2,\alpha_3) = (0.8,1.0,1.2)$.
+\noindent We decided to solve the water-filling problem using \texttt{cvxpy} with $n=3$ channels and $(\alpha_1,\alpha_2,\alpha_3) = (4/5,1,6/5)$.
 For simplicity we chose a dimensionless total power $P=1$.
@@
 With an ordinary commercially available laptop, the time taken to execute the code was around 4ms.
-Note that the code is a little different in formulation from the text in that it maximises the positive sum of $x_i$ rather than minimising the negative.
-The total power constraint is also rearranged.
+Note that the code is a little different in formulation from the text in that it maximises $\sum_{i}^nr_i$ rather than minimising $\sum_{i}^{n}-r_i$.
+The total power constraint is also rearranged to: $\sum_i^nx_i - P = 0$.
 \lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={α}{$\alpha$}1 ]{waterfilling.py}
@@
 This question is relevant to telecom companies who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path-gain matrix, $G$, background noise level vector, $\sigma$, a maximum power constraint, $P_{\text{max}}$, of each transmitter and the fact that all transmitters must be supplied with positive power:
+We formulate the problem with a given square path-gain matrix, $G$, background noise level vector, $\boldsymbol{\sigma} = (\sigma_1, \sigma_2, ..., \sigma_i, ..., \sigma_m)$, a maximum power constraint, $P_{\text{max}}$, of each transmitter and the fact that all transmitters must be supplied with positive power:
 \begin{align*}
@@
 The maximum available power, $P_{\text{max}}$ is set to 1.
-We have chosen the background noise vector $\sigma$ as constant for each receiver, with $\sigma_i = 5$.
+We have chosen the background noise vector $\boldsymbol{\sigma}$ as constant for each receiver, with $\sigma_i = 5$.
 Similarly, the receiver coefficient $A$ was set to $0.025$ for each receiver.

### 2017-12-01 article_cvxpy.tex
just some commas and subscripts added

@@
 \subsection{Path gain}
-\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance $d_{ij}$ between them.
-Assuming isotropic propagation from each transmitter, given a pathloss coefficient $\alpha$ and a proportionality constant $A_i$ specific to receiver $i$, the fraction of power from $j$ that reaches $i$ is,
+\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$, between them.
+Assuming isotropic propagation from each transmitter, given a pathloss coefficient, $\alpha$, and a proportionality constant, $A_i$, specific to receiver $i$, the fraction of power from $j$ that reaches $i$ is,
 \begin{equation}
@@
 The maximum available power, $P_{\text{max}}$ is set to 1.
-We have chosen the background noise vector $\boldsymbol{\sigma}$ as constant for each receiver, with $\sigma_i = 5$.
-Similarly, the receiver coefficient $A$ was set to $0.025$ for each receiver.
+We have chosen the background noise vector, $\boldsymbol{\sigma}$, as constant for each receiver, with $\sigma_i = 5$.
+Similarly, the receiver coefficient, $A_i$, was set to $0.025$ for each receiver.
 \\
 
-To generate the gain matrix $G$, we randomly sample distances from a given distribution.
+To generate the gain matrix, $G$, we randomly sample distances from a given distribution.
 For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.

### 2017-12-01 article_cvxpy.tex
zip files updated

@@
 \noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$, between them.
-Assuming isotropic propagation from each transmitter, given a pathloss coefficient, $\alpha$, and a proportionality constant, $A_i$, specific to receiver $i$, the fraction of power from $j$ that reaches $i$ is,
+Assuming isotropic propagation from each transmitter, given a pathloss coefficient, $\alpha$, and a receiver coefficient, $A_i$, specific to receiver $i$, the fraction of power from $j$ that reaches $i$ is,
 \begin{equation}

### 2018-06-11 article_cvxpy.tex
post proof cvxpy article update

@@
 \noindent Convexity is a fundamentally important property in optimisation.
-Roughly speaking, an optimisation is convex if its objective function is convex, as well the set of points satifying any constraints, and in such cases the task of finding a global minimum is reduced to that of finding a local minimum.
+Roughly speaking, an optimisation problem is convex if its objective function is convex, as well the set of points satifying any constraints, and in such cases the task of finding a global minimum is reduced to that of finding a local minimum.
 The importance of finding these minima efficiently in science and engineering applications has driven the development of software packages, such as \texttt{cvxpy} from the group of Stephen Boyd at Stanford University.
@@
 \caption{\label{fig:convex}The function $f(x)=x^4$ is plotted in blue.
-The convexity of this function can be seen by picking any two values of $x$ and noting that $f(x)$ will always lie below or on the chord connecting these two points.}
+The convexity of this function can be seen by picking any two values of $x$ and noting that $f(x)$ will always lie below or on the orange chord connecting these two points.}
 \end{figure}
@@
  \begin{align}
-  r_i = \log(x_i+\alpha_i).
+  r_i = \log(\alpha_i+x_i).
  \end{align}
@@
  \begin{align}
-\text{minimise} \quad  -&\sum_{i=1}^{n} \log(x_i+\alpha_i) \nonumber \\
+\text{minimise} \quad  -&\sum_{i=1}^{n} \log(\alpha_i+x_i) \nonumber \\
 \text{subject to} \quad &x_i \geqslant 0, \quad \forall i \nonumber \\
@@
  \end{align}
-This is a convex problem since $-\log(x_i+\alpha_i)$ has positive curvature within the domain $x_i \geqslant 0$, and all the constraints are affine and therefore convex.
+This is a convex problem since $-\log(\alpha_i+x_i)$ has positive curvature within the domain $x_i \geqslant 0$, and all the constraints are affine and therefore convex.
 
@@
 \noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below with the parameters chosen above.
-With an ordinary commercially available laptop, the time taken to execute the code was around 4ms.
-Note that the code is a little different in formulation from the text in that it maximises $\sum_{i}^nr_i$ rather than minimising $\sum_{i}^{n}-r_i$.
+With an ordinary commercially-available laptop, the time taken to execute the code was around 4ms.
+Note that the code is a little different in formulation from the text in that it maximises $\sum_{i}^nr_i$ rather than minimising $-\sum_{i}^{n}r_i$.
 The total power constraint is also rearranged to: $\sum_i^nx_i - P = 0$.
@@
 \end{equation}
-For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}.
+For free space $\alpha = 2$, while in urban environments $\alpha \approx 3.5$ \cite{hata1980}.
 Further physical complexities, such as the stochastic effects from Rayleigh fading can be easily incorporated, whilst remaining within the DCP framework.
@@
 To generate the gain matrix, $G$, we randomly sample distances from a given distribution.
-For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.
+For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\text{Beta}(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.
 For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.
@@
 \subsection{Example code}
-\noindent For the random seed of 100 shown in the example code, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
+\noindent For the random seed of 100 shown in the example code, the optimal total power consumption is $P = 0.381$, with $(p_1,p_2,p_3) = (0.139, 0.072, 0.169)$.
 The time taken to find this solution was around 3ms.
-Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\sim0.4$.
+Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\approx0.4$.
 
@@
 \noindent The authors hope that this article shows the utility of \texttt{cvxpy} for simple `toy' problems of real-world relevance.
-$\texttt{cvxpy}$ can handle problems with up to $\sim 10^3$ transmitters, however this takes $\sim 10^{4}-10^{5}\text{ms}$ to run, hence for large real-world problems a faster implementation would likely be required (e.g., a \cpp-based library).
+$\texttt{cvxpy}$ can handle problems with up to $\sim 10^3$ transmitters, however as this takes $\sim 10^{4}-10^{5}\text{ms}$ to run on a modern laptop, for very large real-world problems faster solvers and more computation power would be required.
+Nevertheless, one can solve convex optimisation problems with open-source software, modest computational resources and easily understood code with $\texttt{cvxpy}$.
+%a faster implementation would likely be required (e.g., a \cpp-based library).
 However, there is obviously a trade-off in terms of ease of understanding with these packages.
@@
 \subsection*{Acknowledgements}
-\noindent{}We would like to thank S.~Johnson and S.~Diamond for helpful discussions.
+\noindent{}We would like to thank Samuel Johnson (University of Birmingham) and Steven Diamond (Stanford University) for helpful discussions, and the EPSRC and MRC for funding the University of Warwick Mathematics for Real-World Systems CDT (reference EP/L015374/1).
 

### 2018-06-11 minimisePgivenSINR.py

@@ -12,7 +12,7 @@ d_unpair = np.random.rand(n,n)
 # desired transmitters d∈0.2B[2,2] from receivers
 d_pair = np.random.beta(2,2,size=n)*0.20 
  # make the matrix symmetric
-d = np.tril(d_unpair) + np.tril(d_unpair, -1).T-np.diag(d_unpair)*Δ+d_pair*Δ
+d = np.tril(d_unpair) + np.tril(d_unpair, -1).T-np.diag(d_unpair)*Δ + d_pair*Δ
 
 G = np.zeros((n,n)) # gain matrix G
 G = A / d ** 3.5
@@ -20,7 +20,7 @@ S_hat = G * Δ # signal potential matrix
 I_hat = G - S_hat # interference potential matrix
 
 σ = 5.0 * np.ones(n)
-γ = 1.0 # minimimum acceptable SINR
+γ = 1.0 # minimum acceptable SINR
 Pmax = 1.0 # total power for each transmitter
 
 # Define optimisation variable as the transmitter powers

### 2018-06-11 waterfilling.py

@@ -4,17 +4,15 @@ import numpy as np
 n = 3 # number of channels
 P = 1 # total power available to allocate
 x = cvx.Variable(n) # optimisation variable x
-α = cvx.Parameter(n,sign='positive') # baseline parameter α 
+α = cvx.Parameter(n, sign='positive') # baseline parameter α 
 α.value = [0.8,1.0,1.2]
 
 # Define objective function
-obj = cvx.Maximize(cvx.sum_entries
-                  (cvx.log(α + x))
-                  )
+obj = cvx.Maximize(cvx.sum_entries(cvx.log(α + x)))
 
 # Define constraints
 constraints = [x >= 0,
-               cvx.sum_entries(x) - P ==0]
+               cvx.sum_entries(x) - P == 0]
 
 # Solve problem
 prob = cvx.Problem(obj, constraints)

### 2018-06-15 minimisePgivenSINR.py
updated code to be compatible with cvxpy version > 1.0

@@ -27,7 +27,7 @@ Pmax = 1.0 # total power for each transmitter
 p = cvx.Variable(n)
 
 # Define objective function as the total power
-obj = cvx.Minimize(cvx.sum_entries(p))
+obj = cvx.Minimize(cvx.sum(p))
 
 # Define constraints
 constraints = [p >= 0,

### 2018-06-15 waterfilling.py

@@ -4,15 +4,15 @@ import numpy as np
 n = 3 # number of channels
 P = 1 # total power available to allocate
 x = cvx.Variable(n) # optimisation variable x
-α = cvx.Parameter(n, sign='positive') # baseline parameter α 
+α = cvx.Parameter(n, nonneg=True) # baseline parameter α 
 α.value = [0.8,1.0,1.2]
 
 # Define objective function
-obj = cvx.Maximize(cvx.sum_entries(cvx.log(α + x)))
+obj = cvx.Maximize(cvx.sum(cvx.log(α + x)))
 
 # Define constraints
 constraints = [x >= 0,
-               cvx.sum_entries(x) - P == 0]
+               cvx.sum(x) - P == 0]
 
 # Solve problem
 prob = cvx.Problem(obj, constraints)

### 2018-06-15 article_cvxpy_2017-11-16.tex
Working for new cvxpy in Python3

--- 2017-12-01 article_cvxpy.tex
@@
-% edited Keith Briggs 2017-11-23
 % edited Keith Briggs 2017-11-16
-% latexmk -pdf article_cvxpy && e article_cvxpy.pdf &
+% latexmk -pdf article_cvxpy_2017-11-16 && e article_cvxpy_2017-11-16.pdf &
 
@@
 
-Here we show that real-world problems in communications have convex formulations which can be easily implemented computationally using \texttt{cvxpy}, and coded in Python.
+Here we show that an realistic problem in communications has a convex formulation which can be easily implemented computationally using the \texttt{cvxpy}, and coded in Python.
 This demonstrates \texttt{cvxpy} as an invaluable tool for both students and researchers in many areas of science and engineering, and has the very useful advantage that the program structure closely mirrors the mathematical description of the problem.
@@
 \subsection{Convex functions}
-\noindent{}If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also be in $C$ \cite[p.23]{cvxpybook}.
+\noindent{}If a set $C$ is \textit{convex}, then for any two points $x,y\in C$, any point $z$ along the $x,y$ line must also $\in C$ \cite[p.23]{cvxpybook}.
 More formally, for $x,y\in C$ and $\theta\in [0,1]$:
@@
 \subsection{Disciplined convex programming}
-\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy} (all example code is given for Python 3).
+\noindent In order to solve convex optimisation problems, we used \texttt{cvxpy}, a symbolic programming module for Python \cite{cvxpy}.
 It uses a set of rules, called \textit{disciplined convex programming} (DCP), to determine whether a function is convex.
@@
 %Interior point methods work by applying Newton's algorithm to sequences of equally constrained problems. Is it right that Newton's method is used???
- The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality.
-For more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.
+ The algorithm works by picking a step and direction to travel in the interior of the feasible convex set, such that the solution progresses towards optimality, for more details on barrier methods and primal-dual methods see \citep[p.561]{cvxpybook}.
 
-\section{Example 1: water-filling}
-
-\noindent{}One of the simplest problems to solve in communications with convex optimisation is the classic \textit{water-filling} problem.
-Here a total power $P$ is to be assigned to $n$ different communications channels, with the objective of maximising the total communication rate.
-By Shannon's theorem \citep[p.245]{cvxpybook}, an upper bound for the rate is given by $\log(1+x_i/\alpha_i)$, where $x_i$ is the power allocated to the $i$th channel and $\alpha_i$ is the noise power in that channel.
-This can be written as $\log(\alpha_i+x_i)-\log(\alpha_i)$ and the constants $\log(\alpha_i)$ are disregarded for the purposes of maximization.
-Thus the communication rate, $r_i$, of the $i$th channel without the constant term is given by,
- \begin{align}
-  r_i = \log(x_i+\alpha_i).
- \end{align}
-
-Noting that all power allocations must be non-negative, the optimisation problem can therefore be formulated as,
- \begin{align}
-\text{minimise} \quad  -&\sum_{i=1}^{n} \log(x_i+\alpha_i) \nonumber \\
-\text{subject to} \quad &x_i \geqslant 0, \quad \forall i \nonumber \\
-&\sum_{i=1}^{n}x_i = P.
- \end{align}
-This is a convex problem since $-\log(x_i+\alpha_i)$ has positive curvature within the domain $x_i \geqslant 0$, and all the constraints are affine and therefore convex.
-
-\subsection{Implementation}
-\noindent We decided to solve the water-filling problem using \texttt{cvxpy} with $n=3$ channels and $(\alpha_1,\alpha_2,\alpha_3) = (4/5,1,6/5)$.
-For simplicity we chose a dimensionless total power $P=1$.
-Using these parameters, the maximum communication rate is, $\sum_{i=1}^{n}r_i = 0.863$, which is achieved with power allocations $(x_1,x_2,x_3) = (8/15,5/15,2/15)$.
-This solution is shown in Figure~\ref{fig:waterfilling}, and can be seen as being analogous to filling an uneven basin to a constant level (hence the name \textit{water-filling}).
-
-\subsection{Example Code}
-\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below with the parameters chosen above.
-With an ordinary commercially available laptop, the time taken to execute the code was around 4ms.
-Note that the code is a little different in formulation from the text in that it maximises $\sum_{i}^nr_i$ rather than minimising $\sum_{i}^{n}-r_i$.
-The total power constraint is also rearranged to: $\sum_i^nx_i - P = 0$.
-\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={α}{$\alpha$}1 ]{waterfilling.py}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=1.0\linewidth]{water_filling_plot.pdf}
-\caption{The optimal solution to the water-filling problem allocates the greatest amount of power, $x$, to the channel with the lowest noise power, $\alpha$.}
-\label{fig:waterfilling}
-\end{figure}
-
-\section{Example 2: power minimisation in communications}
+\section{Example: power minimisation in communications}
 \noindent To demonstrate the applicability of \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_k$, ($k=1,2,...,n$) and $m$ receivers, all in two-dimensional Euclidean space \cite{shannon1949}.
-At receiver $i$ there is a power $S_i$ of the desired signal, an interference power $I_i$ from undesired signals, and a background noise $\sigma_i$.
-In this problem we are constrained to having a specified minimum signal-to-interference-plus-noise ratio (SINR or $\gamma_0$) at each receiver, with the SINR at receiver $i$ given by,
+At receiver $i$ there is a power $S_i$ of the desired signal, and an interference power $I_i$ from undesired signals, and a background noise $\sigma$.
+In this problem we are constrained to having a specified minimum signal-to-interference-plus-noise ratio (SINR or $\gamma$) at each receiver
 \begin{equation}
-\gamma_i =\frac{S_i}{I_i+\sigma_i}.
+\gamma_i =\frac{S_i}{I_i+\sigma}.
 \end{equation}
 
-How can we minimise the total power consumption, $P$, of the transmitters, yet achieve this minimum SINR, $\gamma_0$, for all $i$ receivers ($i = 1,2,...,m$)?
+How can we minimise the total power consumption, $P$, of transmitters, yet achieve this minimum SINR, $\gamma_0$, for all $i$ receivers ($i = 1,2,...,m$)?
 This question is relevant to telecom companies who want to offer a service at a minimum quality standard.
-We formulate the problem with a given square path-gain matrix, $G$, background noise level vector, $\boldsymbol{\sigma} = (\sigma_1, \sigma_2, ..., \sigma_i, ..., \sigma_m)$, a maximum power constraint, $P_{\text{max}}$, of each transmitter and the fact that all transmitters must be supplied with positive power:
+We formulate the problem with a given square path-gain matrix, $G$, background noise level vector $\sigma$, a maximum power constraint $P_{\text{max}}$ of each transmitter and the fact that all transmitters must have positive power:
 \begin{align*}
@@
 % The desired signal for receiver $i$ is $S_i = G_{ik}p_k$, 
-While the interference potential matrix is defined as $\hat{I} = G-\hat{S}$, giving the interference at $i$ as $I_i = (\hat{I}*p)_i = \sum_{j\neq k}G_{ij}p_j$.
-We must note that DCP does not allow division of the optimisation variable, $p_i$, as it cannot guarantee curvature, so
+While the interference potential matrix is defined as $\hat{I} = G-\hat{S}$, giving the interference at $i$ is $I_i = (\hat{I}*p)_i = \sum_{j\neq k}G_{ij}p_j$.
+We must note that DCP does not allow division of the optimisation variable $p_i$, as it cannot guarantee curvature, so
 \begin{equation*}
@@
 \subsection{Path gain}
-\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance, $d_{ij}$, between them.
-Assuming isotropic propagation from each transmitter, given a pathloss coefficient, $\alpha$, and a receiver coefficient, $A_i$, specific to receiver $i$, the fraction of power from $j$ that reaches $i$ is,
+%\noindent The path gain $G_{ij}$ represents the proportion of power that reaches receiver $i$ from transmitter $j$.
+Supposing that the desired signal to receiver $i$ is from transmitter $k$, the power received is,
+%\begin{equation}
+%p_{ik}^{\text{rec}} = G_{ik}p_k.
+%\end{equation}
+%Denoting the SINR at $i$ by $\gamma_i$, we have
+%\begin{equation}
+%\gamma_i = \frac{G_{ik}p_k}{\sigma_i+\sum_{j\neq k}G_{ij}p_j}
+%=\frac{S_i}{\sigma_i+I_i}.
+%\end{equation}
+\noindent In a physical context, the path gain from transmitter $j$ to receiver $i$, as shown in Fig.~\ref{fig:pathgain}, will depend on the distance $d_{ij}$ between them.
+Assuming isotropic propagation from each transmitter, the fraction of power from $j$ that reaches $i$ is:
 \begin{equation}
-G_{ij} = A_i/d_{ij}^\alpha.
+G_{ij} = A_i/d_{ij}^\alpha
 \end{equation}
+where $\alpha$ is the pathloss coefficient and $k$ is a proportionality constant specific to the receiver $i$.
 For free space $\alpha = 2$, while in urban environments $\alpha \sim 3.5$ \cite{hata1980}.
@@
 \subsection{Implementation}
-\noindent For ease of terminology, we will make a few simplifying assumptions.
+For ease of terminology, we will make a few simplifying assumptions.
 First, we set the number of transmitters equal to the number of receivers, so $n=m$.
@@
 The maximum available power, $P_{\text{max}}$ is set to 1.
-We have chosen the background noise vector, $\boldsymbol{\sigma}$, as constant for each receiver, with $\sigma_i = 5$.
-Similarly, the receiver coefficient, $A_i$, was set to $0.025$ for each receiver.
+We have chosen the background noise vector $\sigma$ as constant for each receiver, with $\sigma_i = 5$.
+Similarly, the receiver coefficient $A$ was set to $0.025$ for each receiver.
 \\
 
-To generate the gain matrix, $G$, we randomly sample distances from a given distribution.
+To generate the gain matrix $G$, we randomly sample distances from a given distribution.
 For paired transmitters and receivers ($k=i$), we sample $d$ from a scaled $\beta(2,2)$ distribution, such that $d_{ii} \sim 0.2\times\text{Beta}(2,2)$.
 For unpaired transmitters and receivers ($k\neq i$), we sample $d$ from a uniform distribution, such that $d_{ik} \sim \text{Uniform}(0,1)$.
-This is illustrated in Figure~\ref{fig:dist}.
-
-\subsection{Example code}
-\noindent For the random seed of 100 shown in the example code, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
-The time taken to find this solution was around 3ms.
-Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\sim0.4$.
+This is illustrated in Figure \ref{fig:dist}.
 
@@
 
-\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={Δ}{$\Delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}
+\subsection{Example code}
+\noindent To indicate the brevity of code implementation in \texttt{cvxpy} we show a minimal working example below.
+For the random seed of 100 given, the optimal total power consumption is $P = 0.381$, with $p_1,p_2,p_3 = (0.139, 0.072, 0.169)$.
+Around 70\% of the simulations with these parameters have a feasible solution, with an average optimal power consumption of $P\sim0.4$.
+
+\lstinputlisting[language=Python,mathescape=true,inputencoding=utf8,literate={δ}{$\delta$}1 {σ}{$\sigma$}1 {γ}{$\gamma$}1 {∈}{$\in$}1 ]{minimisePgivenSINR.py}
 
@@
 The module could also be easily incorporated into a course on optimisation, providing students with an accessible environment to practise techniques for convex optimisation.
-Full code for other communication examples can be found at \url{https://github.com/cvxgrp/cvxpy/tree/master/examples/communications}.
+Full code for other communication examples can be found at \url{https://github.com/cvxgrp/cvxpy/\\tree/master/examples/communications}.
+
+%While all problems that can be written in DCP are convex, not all convex problems of interest can be written in DCP.
+Over time, the library of available DCP functions in \texttt{cvxpy} has grown, increasing the scope of convex optimisation problems that \texttt{cvxpy} can solve.
+This expansion of scope of \texttt{cvxpy} is ongoing, with version 1.0 under development and expected in the near future.
+
+%\section{Further Work}
+%While many problems are convex, others fall into a similar category of being \textit{quasi-convex}.
+A quasi-convex function $f$ is one for which $\textbf{dom} f$ and every sublevel set of $f$ is convex.
+An example of this is shown in Figure [?].
+Quasi-convex problems cannot be solved directly using convex optimisation solvers, however the feasibility of a sublevel set can be checked.
+This feasibility check can be used as a bisection method to find the solution.
+A more thorough discussion of quasi-convex problems can be found in \cite{cvxpybook}chapter?.
 
@@
 %\section{Links \& references}
-\bibliographystyle{ieeetr}
 \bibliography{articleBib} 
+\bibliographystyle{plain}
 

### 2018-06-15 minimisePgivenSINR.py

@@ -42,5 +42,6 @@ powers = np.asarray(p.value)
 print('Solution status = {0}'.format(prob.status))
 print('Optimal solution = {0:.3f}'.format(prob.value))
 if prob.status == 'optimal':
+  #print(powers[0])
   for j in range(n):
-  	print('Power {0} = {1:.3f}'.format(j,powers[j][0]))
+  	print('Power {0} = {1:.3f}'.format(j,powers[j]))

### 2018-06-15 waterfilling.py

@@ -23,4 +23,4 @@ print('Solution status = {0}'.format(prob.status))
 print('Optimal solution = {0:.3f}'.format(prob.value))
 if prob.status == 'optimal':
   for j in range(n):
-  	print('Power {0} = {1:.3f}'.format(j,powers[j][0]))
+  	print('Power {0} = {1:.3f}'.format(j,powers[j]))
